---
title: "Figure 7 related code"
output: html_notebook
---

## Title : A comprehensive analysis of Transcribed Ultra Conserved Regions uncovers important regulatory functions of novel non coding transcripts in gliomas

## Figure 7

## Set parameters and install required programs
```{r}
## Variables

outputdir <- "Outputs"

filterannot <- "TUCR"

makekpmplots <- TRUE

tpmethod <- "TPM"

repel <- TRUE
```

```{r}
## Load Colors

paper_black = "#000000"
  
paper_gold = "#EAA304"
  
paper_green2 = "#20C799"
  
paper_yellow = "#F0E442"
  
paper_blue = "#017DC3"
  
paper_lightblue = "#58AFE0"
  
paper_skyblue = "#A5DFFF"
  
paper_orange = "#D55E00"
  
paper_purple = "#8C004C"
  
paper_gray = "#CAC4C4"
  
paper_red = "#C30223"
  
paper_darkpink = "#DA7C8C"
  
paper_pink = "#FFCCD5"

paper_green = "#54BB44"
  
paper_red2 = "#CA465C"
  
paper_turq = "#20C799"

```

```{r}
## Load Programs

if (!require("jsonlite")) install.packages("jsonlite")
library("jsonlite")

if (!require("tidyjson")) install.packages("tidyjson")
library("tidyjson")

if (!require("tidyverse")) install.packages("tidyverse")
library("tidyverse")

if (!require("ggplot2")) install.packages("ggplot2")
library("ggplot2")

if (!require("ggforce")) install.packages("ggforce")
library("ggforce")

if (!require("ggbreak")) install.packages("ggbreak")
library("ggbreak")

if (!require("ggrepel")) install.packages("ggrepel")
library("ggrepel")

if (!require("ggfortify")) install.packages("ggfortify")
library("ggfortify")

if (!require("ggdendro")) install.packages("ggdendro")
library("ggdendro")

if (!requireNamespace("BiocManager", quietly = TRUE)) install.packages("BiocManager")
if (!requireNamespace("DESeq2", quietly = TRUE))BiocManager::install("DESeq2")
library("DESeq2")

if (!require("survival")) install.packages("survival")
library("survival")

if (!require("broom")) install.packages("broom")
library("broom")

if (!requireNamespace("limma", quietly = TRUE))BiocManager::install("limma")
library("limma")

if (!require("Tmisc")) install.packages("Tmisc")
library("Tmisc")

if (!require("survminer")) install.packages("survminer")
library("survminer")

if (!require("corrr")) install.packages("corrr")
library("corrr")

if (!require("here")) install.packages("here")
library("here")

if (!require("lessR")) install.packages("lessR")
library("lessR")

if (!require("splitstackshape")) install.packages("splitstackshape")
library(splitstackshape)

if (!requireNamespace("BiocManager", quietly = TRUE)) install.packages("BiocManager")

if (!require('org.Hs.eg.db')) BiocManager::install('org.Hs.eg.db')
library(org.Hs.eg.db)

if (!require('GO.db')) BiocManager::install('GO.db')
library(GO.db)

if (!require('limma')) BiocManager::install('limma')
library(limma)

if (!require("ggthemes")) install.packages('ggthemes', dependencies = TRUE)
library(ggthemes)

if (!require("gplots")) 
install.packages("gplots")
library(gplots)

if (!require("ggsignif")) 
install.packages("ggsignif")
library(ggsignif)

if (!require("RColorBrewer")) 
install.packages("RColorBrewer")
library(RColorBrewer)

if (!require("reshape2")) 
install.packages("reshape2")
library(reshape2)

if (!require("gridExtra")) 
install.packages("gridExtra")
library(gridExtra)

if (!require("dendextend")) 
install.packages("dendextend")
library(dendextend)

if (!require("plyr")) 
install.packages("plyr")
library(plyr)

if (!require("magick")) 
install.packages("magick")
library(magick)

if (!require("png")) 
install.packages("png")
library(png)

if (!require("scales")) 
install.packages("scales")
library(scales)

if (!require("ggsci")) 
install.packages("ggsci")
library(ggsci)

if (!require("stringi")) install.packages("stringi")
  library(stringi)
if (!require("stringr")) install.packages("stringr")
  library(stringr)

if (!require("impute")) BiocManager::install("impute")
library(impute)

if (!require("preprocessCore")) BiocManager::install("preprocessCore")
library(preprocessCore)

if (!require("Go.db")) BiocManager::install("GO.db")
library(GO.db)


if (!require("WGCNA")) install.packages("WGCNA")
library(WGCNA)

if (!require("umap")) install.packages("umap")
library(umap)

if (!require("igraph")) install.packages("igraph")
library(igraph)

if (!require("gtable")) install.packages("gtable")
library(gtable)

if(!dir.exists(outputdir)){
  dir.create(outputdir)
}

knitr::opts_chunk$set(
eval = FALSE,
tidy = TRUE#,
#	echo = TRUE,
#	message = FALSE,
#	warning = FALSE
)

```
## Figure 7

```{r dircreate_Figure7}

dir.create(paste(outputdir,"/Figure7/",sep=""))

```


### Figure 7A, 7B, 7C, and 7F

```{r Figure7af}

Figure7_copy <- list.files("./Inputs/Figure7/pregenerated_figures/")

if(!file.exists(paste(outputdir,"/Figure7/","Figure7ab.png",sep=""))){
  file.copy(paste0("./Inputs/Figure7/pregenerated_figures/",Figure7_copy,sep=""),paste("./",outputdir,"/Figure7/",sep=""))
}

```

### Figure 7D and 7E

```{r Figure7de}

data <- read_csv("./Inputs/Figure7/Figure7de_input.csv") 

data$CellLine <- factor(data$CellLine, levels = c("A172 WT","A172 MUT","U251 WT","U251 MUT"))

p <- ggplot(data,aes(x=reorder(Sample,Order),y=MEAN,fill=reorder(Sample,Order))) +
        geom_bar(stat="identity",position = "dodge") +
        geom_errorbar(aes(ymax=MEAN+SE, ymin=MEAN-SE, width=.2),position = position_dodge(0.9)) +
        geom_text(aes(y = MEAN, label= SIG,vjust=-1.5,hjust=0.5),color = "#000000",size=10,position = position_dodge(0.9)) + 
        scale_fill_manual(values = c(paper_red,paper_blue,paper_red2,paper_yellow)) +
        labs(y = "Relative uc.110/LUC reporter expression",
        x = "") +
        #ylim(-5, 10) +
        theme(plot.title = element_text(size = rel(2.2), hjust = 0.5, face="bold",margin=margin(0,0,0,0)),
              axis.title = element_text(size = rel(1.7), face="bold"),
              axis.text.y = element_text(size = rel(2.2), face="bold"),
              axis.text.x = element_text(size = rel(2.2), face="bold",angle=90,vjust = 0.5, hjust=1),
              #panel.grid = element_line(color = "lightgray",size = 0.75),
panel.background = element_blank(), axis.line = element_line(colour = "black"),legend.position="none",legend.title=element_blank(),
legend.text=element_text(size=rel(2.0)),
strip.text.x = element_text(size = rel(2.2)),
strip.background = element_blank()) + 
  coord_cartesian(clip = "off") +
  facet_wrap(~CellLine,ncol=4)


p

ggsave(file=paste(outputdir,"/Figure7/Figure7de.png",sep=""),
       plot=print(p),
       height = 6,
       width = 8,
       dpi = 700)

```

### Figure 7G and 7H

```{r figure_6gh}

data <- read_csv("Inputs/Figure7/Figure7gh_input.csv") %>%
  dplyr::select(CellLine,Sample,MEAN,SE,SIG,Order)

p <- ggplot(data,aes(x=reorder(Sample,Order), y=MEAN,fill=reorder(Sample,Order))) +
        geom_bar(stat="identity",position = "dodge") +
        geom_errorbar(aes(ymax=MEAN+SE, ymin=MEAN-SE, width=.2),position = position_dodge(0.9)) +
        geom_text(aes(y = MEAN, label= SIG,vjust=-1.5,hjust=0.5),color = "#000000",size=10,position = position_dodge(0.9)) + 
        scale_fill_manual(values = c(paper_red,paper_blue,paper_yellow,paper_red,paper_blue,paper_yellow)) +
        labs(y = "Relative TCF/LUC reporter expression",
        x = "") +
        #ylim(-5, 10) +
        theme(plot.title = element_text(size = rel(2.2), hjust = 0.5, face="bold",margin=margin(0,0,0,0)),
              axis.title = element_text(size = rel(1.6), face="bold"),
              axis.text.y = element_text(size = rel(2.2), face="bold"),
              axis.text.x = element_text(size = rel(2.2), face="bold",angle=90,vjust = 0.5, hjust=1),
              #panel.grid = element_line(color = "lightgray",size = 0.75),
panel.background = element_blank(), axis.line = element_line(colour = "black"),legend.position="none",legend.title=element_blank(),
legend.text=element_text(size=rel(2.0)),
strip.text.x = element_text(size = rel(2.2)),
strip.background = element_blank()) + 
  coord_cartesian(clip = "off") +
  facet_wrap(~CellLine)


p

ggsave(file=paste(outputdir,"/Figure7/Figure7gh.png",sep=""),
       plot=print(p),
       height = 6,
       width = 9,
       dpi = 600)

```

```{r}
sessionInfo()
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.