---
title: 'Uncovering a role for transcribed ultra-conserved regions as long non-coding RNAs in glioblastoma'
author: "Myron Keith Gibert Jr"
date: "January 27, 2020"
output: pdf_document
toc: true
---

```{r setup, results="hide"}
knitr::opts_chunk$set(echo = TRUE)

if (!require("tidyverse")) install.packages("tidyverse")
library("tidyverse")

```

```{r tinytex, include=FALSE}
## INSTALLING LATEX FOR RMARKDOWN

#RMarkdown requires LaTex to create pdf documents as an output. More information can be found [here](https://bookdown.org/yihui/rmarkdown/pdf-document.html). Alternatively, output can be set to "html_document" or "word_document". End users may install LaTex by setting the "wanttinytex" variable to FALSE and running the following script:

#Install tinytex to let RMarkdown create a pdf document? Default: wanttinytex <- FALSE
wanttinytex <- TRUE

if(tinytex:::is_tinytex()==FALSE && wanttinytex == TRUE){
if (!require("tinytex")) install.packages("tinytex")
tinytex::install_tinytex()
}
```

## Introduction
For this first programming assignment I wrote three functions that are meant to interact with dataset that accompanies this assignment. The dataset is contained in a zip file specdata.zip that is included in the GitHub repository.

## Data

```{bash stringtie, eval = FALSE}
wget ftp://ftp.ensembl.org/pub/release-99/gtf/homo_sapiens/Homo_sapiens.GRCh38.99.gtf.gz
mv Homo_sapiens.GRCh38.99.gtf.gz stringtie
gunzip stringtie/Homo_sapiens.GRCh38.99.gtf.gz

module load gcc/7.1.0
module load stringtie/2.0.6

for bam in $(find GBM-RNASEQ-RAW/* -name '*.bam')
do
name=$(echo $bam | awk -F ".bam" '{print $1}')
name2=$(basename "$name")
if [ ! -f stringtie/$name2.gtf ] 
then
    echo "$name2.gtf does not exist"
    stringtie $bam -o $name.gtf
    mv $name.gtf ./stringtie
else
    echo "$name2.gtf exists... skipping"
fi

if [ ! -f $name.gtf ]; then
  stringtie $bam -o $name.gtf
fi
mv $name.gtf ./stringtie
done

cd stringtie

stringtie --merge *rehead.gtf -G Homo_sapiens.GRCh38.99.gtf -o stringtie_merged.gtf

intersectBed -a hg38.ultraConserved.bed -b CHESSgenes.bed -wa -wb > intersectchess_TUCRs.bed

intersectBed -a hg38.ultraConserved.bed -b stringtie_merged.gtf -wa -wb > intersectstringtie_TUCRs.bed

cp stringtie_merged.gtf stringtie_merged.bed
```

```{bash tcga, eval = FALSE}
## Create directory for all outputs from TCGA analysis data
mkdir tcga_analysis/
```

```{bash tcgaheader, eval = FALSE}
## Extract header information from BAM files
# Create directory for extracted headerfiles
mkdir tcga_analysis/head/

# Create extracted header files
for bam in $(find GBM-RNASEQ-RAW/* -name '*.bam')
do
name=$(echo $bam | awk -F ".bam" '{print $1}')
echo $name
samtools view -H $bam > $name.headerids.txt
mv $name.headerids.txt ./tcga_analysis/head/
done
```

```{bash tcgaids, eval = FALSE}
## Get new file names for BAM files using TCGA IDs from extracted header
mkdir tcga_analysis/ids/

# Initialize summary file with TCGA IDs
echo "RAWID,TCGAID" > tcga_analysis/ids/tcgaIDs.csv 

# Extract IDs from header files
for header in $(find tcga_analysis/head/* -name '*headerids.txt')
do
name=$(echo $header | awk -F ".headerids.txt" '{print $1}')
name2=$(echo $name | cut -c20-)
ids1=$(awk '$1=="@RG"{print $3}' $header)
ids2=$(echo $ids1 | cut -c4-)
echo "$name2.bam,$ids2.bam"
echo "$name2.bam,$ids2.bam" > $name.tcgaid.csv
echo "$name2.bam,$ids2.bam" >> tcga_analysis/ids/tcgaIDs.csv 
mv $name.tcgaid.csv ./tcga_analysis/ids/
done
```

```{bash tcgaindex, eval = FALSE}

##Rename BAM files using TCGA ids
# Create folder for new files
mkdir tcga_analysis/reindex/
# Copy BAM files into new directory with updated names

while IFS=, read orig target; do
orig2=$(find GBM-RNASEQ-RAW/* -name $orig)
echo $orig2
cp $orig2 $target
mv $target tcga_analysis/reindex/
done < tcga_analysis/ids/tcgaIDs.csv

# Reindex the renamed files using samtools.
for bam in $(find tcga_analysis/reindex/ -name '*.bam')
do
name=$(echo $bam | awk -F ".bam" '{print $1}')
echo $name
samtools index $bam
done
```

```{bash tcgacounts, eval = FALSE}
mkdir tcga_analysis/foldchange

#Write header line
echo -e chrom"\t"start"\t"end"\t"id tcga_analysis/reindex/*bam | sed -e "s/ /\t/g" > tcga_analysis/foldchange/TUCR_counts.txt

#Counts
multiBamCov -bams tcga_analysis/reindex/*bam -bed hg38.ultraConserved.bed -q 10 >> tcga_analysis/foldchange/TUCR_counts.txt

#Write header line
echo -e chrom"\t"start"\t"end"\t"id *bam | sed -e "s/ /\t/g" > gene_counts.txt

#Counts
multiBamCov -bams *bam -bed CHESSgenes.bed -q 10 >> gene_counts.txt
```

```{bash, eval = FALSE}

wget http://gdac.broadinstitute.org/runs/stddata__2016_01_28/data/GBM/20160128/gdac.broadinstitute.org_GBM.Merge_Clinical.Level_1.2016012800.0.0.tar.gz

tar -xvzf gdac.broadinstitute.org_GBM.Merge_Clinical.Level_1.2016012800.0.0.tar.gz

mv gdac.broadinstitute.org_GBM.Merge_Clinical.Level_1.2016012800.0.0 GBM.Merge_Clinical

```

## Unzipping the data

For this programming assignment I needed to unzip this file and create the directory 'specdata'. Once I unzipped the zip file, I did not make any modifications to the files in the 'specdata' directory. In each file you'll notice that there are many days where either sulfate or nitrate (or both) are missing (coded as NA). This is common with air pollution monitoring data in the United States.

```{r survival}
if(!file.exists("GBM.clin.merged.txt")){unzip("GBM.clin.merged.zip")}

tucrcounts <- read.table("TUCR_counts.txt",header = TRUE)

scal.exp <- function(x){
  res <- matrix(nrow=nrow(x),ncol=ncol(x))
  colnames(res) <- colnames(x)
  rownames(res) <- rownames(x)
  for (i in 1:dim(x)[1]){
    median_n <- median(x[i,])
    for (j in 1:dim(x)[2]){
      if(x[i,j]>median_n){
        res[i,j] <- 1
      }else{
        res[i,j] <- 0
      }
    }
  }
  return(res)
}

scaledata <- tucrcounts[,5:length(colnames(tucrcounts))]
rowdata <- tucrcounts[,1:4]
scaledata <- as.matrix(scaledata)
countdata.exp <- scal.exp(scaledata)
countdata.exp2 <- cbind(rowdata,countdata.exp)

write.csv(countdata.exp2,"countdataexp.csv")

survdata <- read.table("GBM.clin.merged.txt",header = TRUE)
survdata$survival <- as.numeric(survdata$survival)

```

