---
title: "TUCR database related code"
output: html_notebook
---
## Title : A comprehensive analysis of Transcribed Ultra Conserved Regions uncovers important regulatory functions of novel non coding transcripts in gliomas

## TUCR database

### Set parameters and install required programs
```{r}
## Variables

outputdir <- "Outputs"

filterannot <- "TUCR"

makekpmplots <- TRUE

tpmethod <- "TPM"

repel <- TRUE
```

```{r}
## Load Colors

paper_black = "#000000"
  
paper_gold = "#EAA304"
  
paper_green2 = "#20C799"
  
paper_yellow = "#F0E442"
  
paper_blue = "#017DC3"
  
paper_lightblue = "#58AFE0"
  
paper_skyblue = "#A5DFFF"
  
paper_orange = "#D55E00"
  
paper_purple = "#8C004C"
  
paper_gray = "#CAC4C4"
  
paper_red = "#C30223"
  
paper_darkpink = "#DA7C8C"
  
paper_pink = "#FFCCD5"

paper_green = "#54BB44"
  
paper_red2 = "#CA465C"
  
paper_turq = "#20C799"

```

```{r}
## Load Programs

if (!require("jsonlite")) install.packages("jsonlite")
library("jsonlite")

if (!require("tidyjson")) install.packages("tidyjson")
library("tidyjson")

if (!require("tidyverse")) install.packages("tidyverse")
library("tidyverse")

if (!require("ggplot2")) install.packages("ggplot2")
library("ggplot2")

if (!require("ggforce")) install.packages("ggforce")
library("ggforce")

if (!require("ggbreak")) install.packages("ggbreak")
library("ggbreak")

if (!require("ggrepel")) install.packages("ggrepel")
library("ggrepel")

if (!require("ggfortify")) install.packages("ggfortify")
library("ggfortify")

if (!require("ggdendro")) install.packages("ggdendro")
library("ggdendro")

if (!requireNamespace("BiocManager", quietly = TRUE)) install.packages("BiocManager")
if (!requireNamespace("DESeq2", quietly = TRUE))BiocManager::install("DESeq2")
library("DESeq2")

if (!require("survival")) install.packages("survival")
library("survival")

if (!require("broom")) install.packages("broom")
library("broom")

if (!requireNamespace("limma", quietly = TRUE))BiocManager::install("limma")
library("limma")

if (!require("Tmisc")) install.packages("Tmisc")
library("Tmisc")

if (!require("survminer")) install.packages("survminer")
library("survminer")

if (!require("corrr")) install.packages("corrr")
library("corrr")

if (!require("here")) install.packages("here")
library("here")

if (!require("lessR")) install.packages("lessR")
library("lessR")

if (!require("splitstackshape")) install.packages("splitstackshape")
library(splitstackshape)

if (!requireNamespace("BiocManager", quietly = TRUE)) install.packages("BiocManager")

if (!require('org.Hs.eg.db')) BiocManager::install('org.Hs.eg.db')
library(org.Hs.eg.db)

if (!require('GO.db')) BiocManager::install('GO.db')
library(GO.db)

if (!require('limma')) BiocManager::install('limma')
library(limma)

if (!require("ggthemes")) install.packages('ggthemes', dependencies = TRUE)
library(ggthemes)

if (!require("gplots")) 
install.packages("gplots")
library(gplots)

if (!require("ggsignif")) 
install.packages("ggsignif")
library(ggsignif)

if (!require("RColorBrewer")) 
install.packages("RColorBrewer")
library(RColorBrewer)

if (!require("reshape2")) 
install.packages("reshape2")
library(reshape2)

if (!require("gridExtra")) 
install.packages("gridExtra")
library(gridExtra)

if (!require("dendextend")) 
install.packages("dendextend")
library(dendextend)

if (!require("plyr")) 
install.packages("plyr")
library(plyr)

if (!require("magick")) 
install.packages("magick")
library(magick)

if (!require("png")) 
install.packages("png")
library(png)

if (!require("scales")) 
install.packages("scales")
library(scales)

if (!require("ggsci")) 
install.packages("ggsci")
library(ggsci)

if (!require("stringi")) install.packages("stringi")
  library(stringi)
if (!require("stringr")) install.packages("stringr")
  library(stringr)

if (!require("impute")) BiocManager::install("impute")
library(impute)

if (!require("preprocessCore")) BiocManager::install("preprocessCore")
library(preprocessCore)

if (!require("Go.db")) BiocManager::install("GO.db")
library(GO.db)


if (!require("WGCNA")) install.packages("WGCNA")
library(WGCNA)

if (!require("umap")) install.packages("umap")
library(umap)

if (!require("igraph")) install.packages("igraph")
library(igraph)

if (!require("gtable")) install.packages("gtable")
library(gtable)

if(!dir.exists(outputdir)){
  dir.create(outputdir)
}

knitr::opts_chunk$set(
eval = FALSE,
tidy = TRUE#,
#	echo = TRUE,
#	message = FALSE,
#	warning = FALSE
)

```


## Generate FC Plots for each TUCR (GBM)

```{r FC_boxplot_TUCRs_GBM}

disease <- "GBM"

normal <- "cortex"

figureorder <- 1

## read data

t_countfile <- paste("./Inputs/general_files/sequencingfiles/",disease,"/",disease,"_mergedcounts.txt",sep="")

n_countfile <- paste("./Inputs/general_files/sequencingfiles/",normal,"/",normal,"_mergedcounts.txt",sep="")

t_metadatafile <- paste("./Inputs/general_files/sequencingfiles/",disease,"/",disease,"_tcga_metadata.csv",sep="")

n_metadatafile <- paste("./Inputs/general_files/sequencingfiles/",normal,"/",normal,"_gtex_metadata.csv",sep="")

t_seqdepthfile <- paste("./Inputs/general_files/sequencingfiles/",disease,"/",disease,"_seqdepth_counts.csv",sep="")

n_seqdepthfile <- paste("./Inputs/general_files/sequencingfiles/",normal,"/",normal,"_seqdepth_counts.csv",sep="")

## Merge Data

if(!is.na(n_countfile)){
  mergedcounts <- read.table(t_countfile,header = TRUE)
  
  normalcounts <- read.table(n_countfile,header = TRUE) 
  
  mergedcounts <- mergedcounts %>% left_join(normalcounts,by=c("id")) %>%
    dplyr::select(-chrom.y,-start.y,-end.y,-strand.y,-tag.y,-annot.y,-alias.y) %>%
    distinct()
  
  metadata <- 
  read_csv(file = t_metadatafile)
  
  n_metadata <- 
  read_csv(file = n_metadatafile)
  
  rm(normalcounts)
  
  metadata <- rbind(metadata,n_metadata)
  
  rm(n_metadata)
  
  seqdepth <- read.csv(file = t_seqdepthfile)
  
  n_seqdepth <- read.csv(file = n_seqdepthfile)
  
  seqdepth <- rbind(seqdepth,n_seqdepth)
  
  rm(n_seqdepth)
  
  metadata<-metadata[metadata$IDH1status %in% c("normal","WT"),]
  
}else{
    mergedcounts <- read.table(t_countfile,header = TRUE)

    metadata <- read.csv(file = t_metadatafile)
    
    seqdepth <- read.csv(file = t_seqdepthfile)
    
    metadata<-metadata[metadata$IDH1status %in% c("normal","WT"),]
}

if(!dir.exists(paste(outputdir,"/TUCR_Database/",sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/",sep=""))
}

if(!dir.exists(paste(outputdir,"/TUCR_Database/SummaryTables/",sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/SummaryTables/",sep=""))
}

if(!dir.exists(paste(outputdir,"/TUCR_Database/SummaryTables/",disease,sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/SummaryTables/",disease,sep=""))
}

if(!is.na(filterannot)){
  mergedcounts_trimmed <- mergedcounts %>%
  filter(tag.x == filterannot & annot.x != "random")
}

posdata <- mergedcounts_trimmed[,1:8] %>%
  dplyr::select("chrom" = chrom.x,"start" = start.x,"end" = end.x,"strand"=strand.x,id,"alias"=alias.x,"tag"=tag.x,"annot" = annot.x)

mergedcounts_trimmed <- mergedcounts_trimmed[,metadata$survid]

match_colnames <- match(as.character(colnames(mergedcounts_trimmed)),as.character(metadata$survid))

mergedcounts_trimmed <- as.matrix(mergedcounts_trimmed)
rownames(mergedcounts_trimmed) <- posdata$alias

dds <- 
  DESeqDataSetFromMatrix(countData = mergedcounts_trimmed,
                              colData = metadata,
                              design = ~dex)
  
dds <- 
  DESeq(dds)

res <- 
  results(dds, tidy=TRUE)

res <- 
  as_tibble(res)

colnames(res)[1] <- "alias"

#variablename <- which(as.character(colnames(tablename) %in% as.character(row.names(table2name))))

n_index <- which(as.character(metadata$dex) %in% "normal")
t_index <- which(as.character(metadata$dex) %in% "tumor")

vm <- function(x){
  cond <- factor(ifelse(seq(1,dim(x)[2],1) %in% t_index, 1,  0))
  d <- model.matrix(~1+cond)
  x <- t(apply(x,1,as.numeric))
  ex <- voom(x,d,plot=F)
  return(ex$E)
}

count_vm <- vm(mergedcounts_trimmed)

colnames(count_vm) <- colnames(mergedcounts_trimmed)

#if(is.sequential(match_colnames)){
#  print("metadata rows match countfile columns")
#  colnames(count_vm) <- metadata$id
#}else{
#  "metadata rows do not match countfile columns"
#}

scal <- function(x,y){
  median_n <- rowMedians(y)  # mean of normal
  sd_n <- apply(y,1,sd)  # SD of normal
  # z score as (value - mean normal)/SD normal
  res <- matrix(nrow=nrow(x), ncol=ncol(x))
  colnames(res) <- colnames(x)
  rownames(res) <- rownames(x)
  for(i in 1:dim(x)[1]){
    for(j in 1:dim(x)[2]){
      res[i,j] <- (x[i,j]-median_n[i])/sd_n[i]
    }
  }
  return(res)
}

z_rna <- scal(count_vm,count_vm[,n_index])

z_rna2 <- cbind(posdata,z_rna)

write.csv(as.data.frame(z_rna2),file=paste(outputdir,"/TUCR_Database/SummaryTables/",disease,"/",disease,"_zscores_allTUCRs.csv",sep=""),row.names=F)

fc_counts <- cbind(posdata,z_rna) %>%
  dplyr::select(-chrom,-start,-end,-strand)

fc.dotplot <- fc_counts %>% 
  gather(key = "survid", value = "ZScore",-id,-alias,-tag,-annot) %>%
  #mutate(Key = gsub("[.]","-",Sample)) %>%
  #  mutate(string = ifelse(str_detect(Key,"TCGA"),
  #                         sub(".*TCGA", "", Key),
  #                         sub(".*GTEX", "", Key)),
  #         barcode = ifelse(str_detect(Key,"TCGA"),
  #                          tolower(paste("TCGA",substr(string, 1, 8),sep="")),
  #                          tolower(paste("GTEX",substr(string, 1, 20),sep="")))) %>%
  left_join(metadata,by="survid")

fc.dotplot <- fc.dotplot %>%
  left_join(res,by="alias") %>%
  mutate(DESeq2 = ifelse(dex=="normal",0,log2FoldChange)) %>%
  mutate(fill = ifelse(DESeq2 >= 1,paper_red,
                ifelse(DESeq2 <= -1,paper_green,paper_gray))) %>%
  dplyr::select(-id.y,-log2FoldChange) %>%
  filter(!is.na(dex))

fc.dotplot2 <- fc.dotplot %>%
  filter(str_detect(id.x,"uc.110"))


for(i in 1:length(unique(fc.dotplot$id.x))){
  
filterdotplot <- as.character(unique(fc.dotplot$id.x[i]))

print(i)

fc.dotplot2 <- fc.dotplot %>%
  filter(id.x == filterdotplot)


print(fc.dotplot2$alias[1])
TUCRname <- fc.dotplot2$alias[1]

if(!dir.exists(paste(outputdir,"/TUCR_Database/",TUCRname,"/",sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/",TUCRname,"/",sep=""))
}

#if(file.exists(paste(outputdir,"/TUCR_Database/",TUCRname,"/",figureorder,"_",TUCRname,"_",disease,"_FC_plot.png",sep = ""))){}else{


padj.DESeq2 <- fc.dotplot2 %>%
  filter(dex == "tumor") %>%
  dplyr::select(padj)

padj.DESeq2 <- formatC(padj.DESeq2[[1]][1], format = "e", digits = 2)

foldchange.DESeq2 <- fc.dotplot2 %>%
  filter(dex == "tumor") %>%
  dplyr::select(DESeq2)

foldchange.DESeq2 <- round(foldchange.DESeq2[1,1],2)

fc.dotplot3 <- fc.dotplot2 %>%
  dplyr::select(dex,DESeq2,fill) %>%
  distinct()

p2 <- ggplot(data = fc.dotplot2,aes(x=dex, y=ZScore,fill=fill)) +
  geom_boxplot(outlier.color="white") +
  #geom_bar(colour="black",stat="identity") +
  scale_fill_identity() +
  #scale_color_manual(values = c("black"="black","red"="red","green"="green")) +
  geom_jitter(data = fc.dotplot2, aes(x=dex, y=ZScore),binaxis='y', stackdir='center', stackratio=0.90, dotsize=0.30,fill="gray",width=0.2) +
  ggtitle(paste0(disease,"\n","FC = ",round(foldchange.DESeq2,2),"\n","FDR = ",padj.DESeq2)) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        plot.title = element_text(size = rel(2.2), hjust = 0.5, face="bold",margin=margin(0,0,0,0)),
        axis.title = element_text(size = rel(1.6), face="bold"),
        axis.text.y = element_text(size = rel(2.2)),
        axis.text.x = element_text(size = rel(2.2),angle=90,vjust = 0.5, hjust=1),
              #panel.grid = element_line(color = "lightgray",size = 0.75),
        legend.position="none",
        legend.title=element_text(size = rel(1.6), hjust = 0.5, face="bold",margin=margin(0,0,0,0))) +
  labs(y="Z-Score", x = "Tissue Type") +
  stat_summary(fun.y=mean, geom="point", shape=20, size=6, color=paper_blue, fill=paper_blue)

ggsave(p2,file=(paste(outputdir,"/TUCR_Database/",TUCRname,"/",figureorder,"_",TUCRname,"_",disease,"_FC_plot.png",sep = "")),height=7,width=5)

}

```



## Generate FC Plots for each TUCR (LGG)

```{r FC_boxplot_TUCRs_LGG}

disease <- "LGG"

normal <- "cortex"

figureorder <- 2

# read data

t_countfile <- paste("./Inputs/general_files/sequencingfiles/",disease,"/",disease,"_mergedcounts.txt",sep="")

n_countfile <- paste("./Inputs/general_files/sequencingfiles/",normal,"/",normal,"_mergedcounts.txt",sep="")

t_metadatafile <- paste("./Inputs/general_files/sequencingfiles/",disease,"/",disease,"_tcga_metadata.csv",sep="")

n_metadatafile <- paste("./Inputs/general_files/sequencingfiles/",normal,"/",normal,"_gtex_metadata.csv",sep="")

t_seqdepthfile <- paste("./Inputs/general_files/sequencingfiles/",disease,"/",disease,"_seqdepth_counts.csv",sep="")

n_seqdepthfile <- paste("./Inputs/general_files/sequencingfiles/",normal,"/",normal,"_seqdepth_counts.csv",sep="")

# Merge Data

if(!is.na(n_countfile)){
  mergedcounts <- read.table(t_countfile,header = TRUE)
  
  normalcounts <- read.table(n_countfile,header = TRUE) 
  
  mergedcounts <- mergedcounts %>% left_join(normalcounts,by=c("id")) %>%
    dplyr::select(-chrom.y,-start.y,-end.y,-strand.y,-tag.y,-annot.y,-alias.y) %>%
    distinct()
  
  metadata <- 
  read_csv(file = t_metadatafile)
  
  n_metadata <- 
  read_csv(file = n_metadatafile)
  
  rm(normalcounts)
  
  metadata <- rbind(metadata,n_metadata)
  
  rm(n_metadata)
  
  seqdepth <- read.csv(file = t_seqdepthfile)
  
  n_seqdepth <- read.csv(file = n_seqdepthfile)
  
  seqdepth <- rbind(seqdepth,n_seqdepth)
  
  rm(n_seqdepth)
  
}else{
    mergedcounts <- read.table(t_countfile,header = TRUE)

    metadata <- read.csv(file = t_metadatafile)
    
    seqdepth <- read.csv(file = t_seqdepthfile)
}

if(!dir.exists(paste(outputdir,"/TUCR_Database/",sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/",sep=""))
}

if(!dir.exists(paste(outputdir,"/TUCR_Database/SummaryTables/",sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/SummaryTables/",sep=""))
}

if(!dir.exists(paste(outputdir,"/TUCR_Database/SummaryTables/",disease,sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/SummaryTables/",disease,sep=""))
}

if(!is.na(filterannot)){
  mergedcounts_trimmed <- mergedcounts %>%
  filter(tag.x == filterannot & annot.x != "random")
}

posdata <- mergedcounts_trimmed[,1:8] %>%
  dplyr::select("chrom" = chrom.x,"start" = start.x,"end" = end.x,"strand"=strand.x,id,"alias"=alias.x,"tag"=tag.x,"annot" = annot.x)

mergedcounts_trimmed <- mergedcounts_trimmed[,metadata$survid]

mergedcounts_trimmed <- as.matrix(mergedcounts_trimmed)
rownames(mergedcounts_trimmed) <- posdata$alias

# LGG_WT

metadata_wt <-metadata[metadata$IDH1status %in% c("normal","WT"),]
                      
mergedcounts_trimmed_wt<-mergedcounts_trimmed[,metadata_wt$survid]

#match_colnames <- match(as.character(colnames(mergedcounts_trimmed)),as.character(metadata$survid))

dds <- 
  DESeqDataSetFromMatrix(countData = mergedcounts_trimmed_wt,
                              colData = metadata_wt,
                              design = ~dex)

dds <- 
  DESeq(dds)

res <- 
  results(dds, tidy=TRUE)

res_wt <- 
  as_tibble(res)

colnames(res_wt)[1] <- "alias"

# LGG_MUT

metadata_mut <-metadata[metadata$IDH1status %in% c("normal","WT"),]
                      
mergedcounts_trimmed_mut<-mergedcounts_trimmed[,metadata_mut$survid]

match_colnames <- match(as.character(colnames(mergedcounts_trimmed)),as.character(metadata$survid))

mergedcounts_trimmed <- as.matrix(mergedcounts_trimmed)
rownames(mergedcounts_trimmed) <- posdata$alias


dds <- 
  DESeqDataSetFromMatrix(countData = mergedcounts_trimmed_mut,
                              colData = metadata_mut,
                              design = ~dex)

dds <- 
  DESeq(dds)

res <- 
  results(dds, tidy=TRUE)

res_mut <- 
  as_tibble(res)

colnames(res_mut)[1] <- "alias"

#variablename <- which(as.character(colnames(tablename) %in% as.character(row.names(table2name))))

n_index <- which(as.character(metadata$dex) %in% "normal")
t_index <- which(as.character(metadata$dex) %in% "tumor")

vm <- function(x){
  cond <- factor(ifelse(seq(1,dim(x)[2],1) %in% t_index, 1,  0))
  d <- model.matrix(~1+cond)
  x <- t(apply(x,1,as.numeric))
  ex <- voom(x,d,plot=F)
  return(ex$E)
}

count_vm <- vm(mergedcounts_trimmed)

colnames(count_vm) <- colnames(mergedcounts_trimmed)

#if(is.sequential(match_colnames)){
#  print("metadata rows match countfile columns")
#  colnames(count_vm) <- metadata$id
#}else{
#  "metadata rows do not match countfile columns"
#}

scal <- function(x,y){
  median_n <- rowMedians(y)  # mean of normal
  sd_n <- apply(y,1,sd)  # SD of normal
  # z score as (value - mean normal)/SD normal
  res <- matrix(nrow=nrow(x), ncol=ncol(x))
  colnames(res) <- colnames(x)
  rownames(res) <- rownames(x)
  for(i in 1:dim(x)[1]){
    for(j in 1:dim(x)[2]){
      res[i,j] <- (x[i,j]-median_n[i])/sd_n[i]
    }
  }
  return(res)
}

z_rna <- scal(count_vm,count_vm[,n_index])

z_rna2 <- cbind(posdata,z_rna)

#write.csv(as.data.frame(z_rna2),file=paste(outputdir,"/TUCR_Database/SummaryTables/",disease,"/",disease,"_zscores_allTUCRs.csv",sep=""),row.names=F)

fc_counts <- cbind(posdata,z_rna) %>%
  dplyr::select(-chrom,-start,-end,-strand)

fc.dotplot <- fc_counts %>% 
  gather(key = "survid", value = "ZScore",-id,-alias,-tag,-annot) %>%
  #mutate(Key = gsub("[.]","-",Sample)) %>%
  #  mutate(string = ifelse(str_detect(Key,"TCGA"),
  #                         sub(".*TCGA", "", Key),
  #                         sub(".*GTEX", "", Key)),
  #         barcode = ifelse(str_detect(Key,"TCGA"),
  #                          tolower(paste("TCGA",substr(string, 1, 8),sep="")),
  #                          tolower(paste("GTEX",substr(string, 1, 20),sep="")))) %>%
  left_join(metadata,by="survid")

  fc.dotplot <- fc.dotplot %>%
  left_join(res_wt,by="alias") %>%
  mutate(DESeq2_wt = ifelse(dex=="normal",0,log2FoldChange)) %>%
  mutate(padj_wt=padj) %>% 
  mutate(fill_wt = ifelse(DESeq2_wt >= 1,paper_red,
                ifelse(DESeq2_wt <= -1,paper_green,paper_gray))) %>%
  dplyr::select(-id.y,-log2FoldChange,-lfcSE,-stat,-padj,-baseMean,-pvalue)
  

## we adressed na values while joining metadata and zscore values 
## so removed filter(!is.na(dex)) from above step

## Adding lgg_mut vs normal deseq2 foldchange and padj values to the main dataset
  
  fc.dotplot <- fc.dotplot %>%
  left_join(res_mut,by="alias") %>%
  mutate(DESeq2_mut = ifelse(dex=="normal",0,log2FoldChange)) %>%
  mutate(padj_mut=padj) %>% 
  mutate(fill_mut = ifelse(DESeq2_mut >= 1,paper_pink,
                ifelse(DESeq2_mut <= -1,paper_blue,paper_gray))) %>%
  dplyr::select(-log2FoldChange,-lfcSE,-stat)
  
  
## combine DeSeq2_wt and DeSeq2_mut in to DeSeq2 using ifelse
## combine padj_wt and padj_mut in to padj column using if else

  fc.dotplot <- fc.dotplot %>%
    mutate(DESeq= ifelse(IDH1status=="MUT",DESeq2_mut,DESeq2_wt)) %>%
    mutate(padj=ifelse(IDH1status=="MUT",padj_mut,padj_wt)) %>% 
    mutate(fill= ifelse(IDH1status=="MUT",fill_mut,fill_wt)) 
  

for(i in 1:length(unique(fc.dotplot$id.x))){
  
filterdotplot <- as.character(unique(fc.dotplot$id.x[i]))

print(i)

fc.dotplot2 <- fc.dotplot %>%
filter(id.x == filterdotplot)

TUCRname <- fc.dotplot2$alias[1]

if(!dir.exists(paste(outputdir,"/TUCR_Database/",TUCRname,"/",sep=""))){
 dir.create(paste(outputdir,"/TUCR_Database/",TUCRname,"/",sep=""))
}

#if(file.exists(paste(outputdir,"/TUCR_Database/",TUCRname,"/",figureorder,"_",TUCRname,"_",disease,"_FC_plot.png",sep = ""))){}else{


## padj.DESeq2 for LGG wt type
padj.DESeq2_wt <- fc.dotplot2 %>%
  filter(IDH1status == "WT") %>%
  dplyr::select(padj_wt)

padj.DESeq2_wt <- formatC(padj.DESeq2_wt[[1]][1], format = "e", digits = 2)

## padj.DESeq2 for LGG mut type
padj.DESeq2_mut <- fc.dotplot2 %>%
  filter(IDH1status == "MUT") %>%
  dplyr::select(padj_mut)

padj.DESeq2_mut <- formatC(padj.DESeq2_mut[[1]][1], format = "e", digits = 2)


foldchange.DESeq2_wt <- fc.dotplot2 %>%
  filter(IDH1status == "WT") %>%
  dplyr::select(DESeq2_wt)

foldchange.DESeq2_wt <- round(foldchange.DESeq2_wt[1,1],2)

foldchange.DESeq2_mut <- fc.dotplot2 %>%
  filter(IDH1status == "MUT") %>%
  dplyr::select(DESeq2_mut)

foldchange.DESeq2_mut <- round(foldchange.DESeq2_mut[1,1],2)


#fc.dotplot3 <- fc.dotplot2 %>%
  #dplyr::select(IDH1status,DESeq,fill) %>%
  #distinct()

## ordering levels of IDH status (Normal,WT,MUT)

fc.dotplot2$IDH1status<-factor(fc.dotplot2$IDH1status,levels=c("normal","WT","MUT"))

p2 <- ggplot(data = fc.dotplot2,aes(x=IDH1status, y=ZScore,fill=fill)) +
  geom_boxplot(outlier.color="white") +
  #geom_bar(colour="black",stat="identity") +
  scale_fill_identity() +
  #scale_color_manual(values = c("black"="black","red"="red","green"="green")) +
  geom_jitter(data = fc.dotplot2, aes(x=IDH1status, y=ZScore),binaxis='y', stackdir='center', stackratio=0.90, dotsize=0.30,fill="gray",width=0.2) +
  ggtitle(paste0(disease,"\n","FC_wt = ",round(foldchange.DESeq2_wt,2),"\n","FDR_wt = ",padj.DESeq2_wt)) +
  #ggtitle(paste0(disease,"\n")) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        plot.title = element_text(size = rel(2.1), hjust = 0.5, face="bold",margin=margin(0,0,0,0)),
        axis.title = element_text(size = rel(1.2), face="bold"),
        axis.text.y = element_text(size = rel(2.2)),
        axis.text.x = element_text(size = rel(2.2),angle=90,vjust = 0.5, hjust=1),
              #panel.grid = element_line(color = "lightgray",size = 0.75),
        legend.position="none",
        legend.title=element_text(size = rel(1.6), hjust = 0.5, face="bold",margin=margin(0,0,0,0))) +
  labs(y="Z-Score", x = "IDH1 status") +
  stat_summary(fun.y=mean, geom="point", shape=20, size=6, color=paper_blue, fill=paper_blue) 

p2
  
ggsave(p2,file=(paste(outputdir,"/TUCR_Database/",TUCRname,"/",figureorder,"_",TUCRname,"_",disease,"_FC_plot.png",sep = "")),height=7,width=5)

}


```

## Generate tpm Box Plots for each TUCR (GBM)

```{r tpm_boxplot_GBM_TUCRs}

disease <- "GBM"

normal <- "cortex"

figureorder <- 3

# read data

t_countfile <- paste("./Inputs/general_files/sequencingfiles/",disease,"/",disease,"_mergedcounts.txt",sep="")

n_countfile <- paste("./Inputs/general_files/sequencingfiles/",normal,"/",normal,"_mergedcounts.txt",sep="")

t_metadatafile <- paste("./Inputs/general_files/sequencingfiles/",disease,"/",disease,"_tcga_metadata.csv",sep="")

n_metadatafile <- paste("./Inputs/general_files/sequencingfiles/",normal,"/",normal,"_gtex_metadata.csv",sep="")

t_seqdepthfile <- paste("./Inputs/general_files/sequencingfiles/",disease,"/",disease,"_seqdepth_counts.csv",sep="")

n_seqdepthfile <- paste("./Inputs/general_files/sequencingfiles/",normal,"/",normal,"_seqdepth_counts.csv",sep="")

# Merge Data

if(!is.na(n_countfile)){
  mergedcounts <- read.table(t_countfile,header = TRUE)
  
  normalcounts <- read.table(n_countfile,header = TRUE) 
  
  mergedcounts <- mergedcounts %>% left_join(normalcounts,by=c("id")) %>%
    dplyr::select(-chrom.y,-start.y,-end.y,-strand.y,-tag.y,-annot.y,-alias.y) %>%
    distinct()
  
  metadata <- 
  read_csv(file = t_metadatafile)
  
  n_metadata <- 
  read_csv(file = n_metadatafile)
  
  rm(normalcounts)
  
  metadata <- rbind(metadata,n_metadata)
  
  rm(n_metadata)
  
  seqdepth <- read.csv(file = t_seqdepthfile)
  
  n_seqdepth <- read.csv(file = n_seqdepthfile)
  
  seqdepth <- rbind(seqdepth,n_seqdepth)
  
  rm(n_seqdepth)
  
  metadata<-metadata[metadata$IDH1status %in% c("normal","WT"),]
  
}else{
    mergedcounts <- read.table(t_countfile,header = TRUE)

    metadata <- read.csv(file = t_metadatafile)
    
    seqdepth <- read.csv(file = t_seqdepthfile)
    
    metadata<-metadata[metadata$IDH1status %in% c("normal","WT"),]
}

if(!dir.exists(paste(outputdir,"/TUCR_Database/",sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/",sep=""))
}

if(!dir.exists(paste(outputdir,"/TUCR_Database/SummaryTables/",sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/SummaryTables/",sep=""))
}

if(!dir.exists(paste(outputdir,"/TUCR_Database/SummaryTables/",disease,"/",sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/SummaryTables/",disease,"/",sep=""))
}

#if(makeRPKboxplots == TRUE){
  
if(!is.na(filterannot)){
  tpmcounts <- mergedcounts %>%
  filter(tag.x == filterannot & annot.x != "random") %>%
  mutate(length = end.x - start.x)
}else{
tpmcounts <- mergedcounts %>%
  mutate(length = end.x - start.x)}

tpmcounts.info <- tpmcounts %>%
  dplyr::select("chrom" = chrom.x,"start" = start.x,"end" = end.x,"strand"=strand.x,id,"alias"=alias.x,"tag"=tag.x,"annot" = annot.x,length)

tpmcounts <- tpmcounts %>%
  dplyr::select(-chrom.x,-start.x,-end.x,-id,-strand.x,-tag.x,-annot.x,-alias.x)
  
rownames(tpmcounts) <- as.character(tpmcounts.info$id)

genelength <- tpmcounts.info$length/1000

seqdepth2 <- as.vector(seqdepth$counts)/1000000

tpm <- function(counts,len,dep){
  #x <- tpmcounts/genelength
  #x2 <- t(t(x)/(seqdepth2))
  x <- counts/len
  return(t(t(x)/(dep)))
}

tpm.df <- tpm(tpmcounts,genelength,seqdepth2)

tpm.df2 <- cbind(tpmcounts.info,tpm.df)

tpm.median <- as.data.frame(tpm.df)
tpm.median <- tpm.median %>% 
  dplyr::summarize(median_tpm = rowMedians(tpm.df)) %>%
  dplyr::mutate(countif = ifelse(median_tpm >=1,1,0),proportion = sum(countif,na.rm = TRUE)/n())
tpm.median <- cbind(tpmcounts.info,tpm.median)
tpm.median <- tpm.median %>% dplyr::select(id,median_tpm,countif,proportion)

proportion.df <- round(as.numeric(tpm.median$proportion[1]),3)*100

write.csv(tpm.df2,paste(outputdir,"/TUCR_Database/SummaryTables/",disease,"/",disease,"_tpms_allTUCRs.csv",sep=""),row.names=F)

tpm.median.write <- tpm.median[,-3]

tpm.median.write <- tpm.median.write[,-3]

tpm.median.write <- tpmcounts.info %>%
  left_join(tpm.median.write,by="id")

write.csv(tpm.median.write,paste(outputdir,"/TUCR_Database/SummaryTables/",disease,"/",disease,"_median_tpm_allTUCRs.csv",sep=""),row.names=F)
  
tpm.dotplot <- tpm.df2[,metadata$survid]
TUCRids <- as.character(tpm.df2$id)
annot <- as.character(tpm.df2$annot)
length <- as.character(tpm.df2$length)
tpm.dotplot <- cbind(TUCRids,annot,length,tpm.dotplot)

tpm.dotplot <- tpm.dotplot %>% 
  gather(key = "survid", value = "TPM",-TUCRids,-annot,-length,-length) %>%
  #mutate(Key = gsub("[.]","-",Sample)) %>%
  #  mutate(string = ifelse(str_detect(Key,"TCGA"),
  #                         sub(".*TCGA", "", Key),
  #                         sub(".*GTEX", "", Key)),
  #         barcode = ifelse(str_detect(Key,"TCGA"),
  #                          tolower(paste("TCGA",substr(string, 1, 8),sep="")),
  #                          tolower(paste("GTEX",substr(string, 1, 20),sep="")))) %>%
  left_join(metadata,by="survid")

tpm.dotplot <- tpm.dotplot[complete.cases(tpm.dotplot),]

median(tpm.dotplot$TPM,na.rm=TRUE)

for(i in 1:length(TUCRids)){
TUCR <- "uc.110"
TUCR <- tpm.df2$id[i]
TUCRname <- as.character(tpm.df2$alias[i])
#print(i)
#print(TUCRname)
if(!dir.exists(paste(outputdir,"/TUCR_Database/",TUCRname,"/",sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/",TUCRname,"/",sep=""))
}
#if(file.exists(paste(outputdir,"/TUCR_Database/",TUCRname,"/",figureorder,"_",TUCRname,"_",disease,"_tpm_boxplot.png",sep = ""))){}else{
tpm.dotplot2 <- tpm.dotplot %>% dplyr::filter(TUCRids == TUCR)

p<- ggplot(tpm.dotplot2, aes(x=dex, y=TPM)) +
  geom_boxplot(outlier.color="white") +
  #geom_violin(trim = FALSE)+
  #geom_point(pch=21, size=1.5) +
  geom_jitter(binaxis='y', stackdir='center', stackratio=0.90, dotsize=0.30,fill="gray",width=0.2) +
  ggtitle(paste(tpmethod," expression of ",TUCR)) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        plot.title = element_text(size = rel(2.2), hjust = 0.5, face="bold",margin=margin(0,0,0,0)),
        axis.title = element_text(size = rel(1.6), face="bold"),
        axis.text.y = element_text(size = rel(2.2)),
        axis.text.x = element_text(size = rel(2.2),angle=90,vjust = 0.5, hjust=1),
              #panel.grid = element_line(color = "lightgray",size = 0.75),
        legend.position="none",
        legend.title=element_blank(),
        legend.text=element_blank()) +
        labs(y=paste(ifelse((tpmethod=="tpm"|tpmethod=="TPM"),
                      "Transcripts per kilobase million (TPM)",
                      "Reads per kilobase million (tpm)")),
        x = "Sample",title=disease) +
  stat_summary(fun.y=mean, geom="point", shape=20, size=10, color=paper_blue, fill=paper_blue)

ggsave(p,file=paste(outputdir,"/TUCR_Database/",TUCRname,"/",figureorder,"_",TUCRname,"_",disease,"_tpm_boxplot.png",sep = ""),height=7,width=5)

}



```

## Generate tpm Box Plots for each TUCR
## LGG
```{r TPM_boxplot_LGG_TUCRs}

disease <- "LGG"

normal <- "cortex"

figureorder <- 4

# read data

t_countfile <- paste("./Inputs/general_files/sequencingfiles/",disease,"/",disease,"_mergedcounts.txt",sep="")

n_countfile <- paste("./Inputs/general_files/sequencingfiles/",normal,"/",normal,"_mergedcounts.txt",sep="")

t_metadatafile <- paste("./Inputs/general_files/sequencingfiles/",disease,"/",disease,"_tcga_metadata.csv",sep="")

n_metadatafile <- paste("./Inputs/general_files/sequencingfiles/",normal,"/",normal,"_gtex_metadata.csv",sep="")

t_seqdepthfile <- paste("./Inputs/general_files/sequencingfiles/",disease,"/",disease,"_seqdepth_counts.csv",sep="")

n_seqdepthfile <- paste("./Inputs/general_files/sequencingfiles/",normal,"/",normal,"_seqdepth_counts.csv",sep="")

# Merge Data

if(!is.na(n_countfile)){
  mergedcounts <- read.table(t_countfile,header = TRUE)
  
  normalcounts <- read.table(n_countfile,header = TRUE) 
  
  mergedcounts <- mergedcounts %>% left_join(normalcounts,by=c("id")) %>%
    dplyr::select(-chrom.y,-start.y,-end.y,-strand.y,-tag.y,-annot.y,-alias.y) %>%
    distinct()
  
  metadata <- 
  read_csv(file = t_metadatafile)
  
  n_metadata <- 
  read_csv(file = n_metadatafile)
  
  rm(normalcounts)
  
  metadata <- rbind(metadata,n_metadata)
  
  rm(n_metadata)
  
  seqdepth <- read.csv(file = t_seqdepthfile)
  
  n_seqdepth <- read.csv(file = n_seqdepthfile)
  
  seqdepth <- rbind(seqdepth,n_seqdepth)
  
  rm(n_seqdepth)
  
}else{
    mergedcounts <- read.table(t_countfile,header = TRUE)

    metadata <- read.csv(file = t_metadatafile)
    
    seqdepth <- read.csv(file = t_seqdepthfile)
}

if(!dir.exists(paste(outputdir,"/TUCR_Database/",sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/",sep=""))
}

if(!dir.exists(paste(outputdir,"/TUCR_Database/SummaryTables/",sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/SummaryTables/",sep=""))
}

if(!dir.exists(paste(outputdir,"/TUCR_Database/SummaryTables/",disease,"/",sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/SummaryTables/",disease,"/",sep=""))
}

#if(makeRPKboxplots == TRUE){
  
if(!is.na(filterannot)){
  tpmcounts <- mergedcounts %>%
  filter(tag.x == filterannot & annot.x != "random") %>%
  mutate(length = end.x - start.x)
}else{
tpmcounts <- mergedcounts %>%
  mutate(length = end.x - start.x)}

tpmcounts.info <- tpmcounts %>%
  dplyr::select("chrom" = chrom.x,"start" = start.x,"end" = end.x,"strand"=strand.x,id,"alias"=alias.x,"tag"=tag.x,"annot" = annot.x,length)

tpmcounts <- tpmcounts %>%
  dplyr::select(-chrom.x,-start.x,-end.x,-id,-strand.x,-tag.x,-annot.x,-alias.x,-length)
  
rownames(tpmcounts) <- as.character(tpmcounts.info$id)

genelength <- tpmcounts.info$length/1000

seqdepth2 <- as.vector(seqdepth$counts)/1000000

tpm <- function(counts,len,dep){
  #x <- tpmcounts/genelength
  #x2 <- t(t(x)/(seqdepth2))
  x <- counts/len
  return(t(t(x)/(dep)))
}

tpm.df <- tpm(tpmcounts,genelength,seqdepth2)

tpm.df2 <- cbind(tpmcounts.info,tpm.df)

tpm.median <- as.data.frame(tpm.df)
tpm.median <- tpm.median %>% 
  dplyr::summarize(median_tpm = rowMedians(tpm.df)) %>%
  dplyr::mutate(countif = ifelse(median_tpm >=1,1,0),proportion = sum(countif,na.rm = TRUE)/n())
tpm.median <- cbind(tpmcounts.info,tpm.median)
tpm.median <- tpm.median %>% dplyr::select(id,median_tpm,countif,proportion)

proportion.df <- round(as.numeric(tpm.median$proportion[1]),3)*100

tpm.df.write <- cbind(tpmcounts.info,tpm.df2)

write.csv(tpm.df.write,paste(outputdir,"/TUCR_Database/SummaryTables/",disease,"/",disease,"_tpms_allTUCRs.csv",sep=""),row.names=F)

tpm.median.write <- tpm.median[,-3]

tpm.median.write <- tpm.median.write[,-3]

tpm.median.write <- tpmcounts.info %>%
  left_join(tpm.median.write,by="id")

write.csv(tpm.median.write,paste(outputdir,"/TUCR_Database/SummaryTables/",disease,"/",disease,"_median_tpm_allTUCRs.csv",sep=""),row.names=F)

tpm.dotplot <- tpm.df2[,9:ncol(tpm.df2)]
TUCRids <- as.character(tpm.df2$id)
annot <- as.character(tpm.df2$annot)
length <- as.character(tpm.df2$length)
tpm.dotplot <- cbind(TUCRids,annot,length,tpm.dotplot)

tpm.dotplot<-tpm.dotplot[,c(1,2,3,5:768)]
tpm.dotplot <- tpm.dotplot %>% 
  gather(key = "survid", value = "TPM",-TUCRids,-annot,-length) %>%
  #gather(key = "Sample", value = "TPM",-TUCRids,-annot,-length) %>%
  #mutate(Key = gsub("[.]","-",Sample)) %>%
  #  mutate(string = ifelse(str_detect(Key,"TCGA"),
  #                         sub(".*TCGA", "", Key),
  #                         sub(".*GTEX", "", Key)),
  #         barcode = ifelse(str_detect(Key,"TCGA"),
  #                          tolower(paste("TCGA",substr(string, 1, 8),sep="")),
  #                          tolower(paste("GTEX",substr(string, 1, 20),sep="")))) %>%
  left_join(metadata,by="survid")

tpm.dotplot <- tpm.dotplot[complete.cases(tpm.dotplot),]

median(tpm.dotplot$TPM,na.rm=TRUE)


for(i in 1:length(TUCRids)){
  
TUCR <- tpm.df2$id[i]
TUCRname <- as.character(tpm.df2$alias[i])
print(i)
print(TUCRname)
if(!dir.exists(paste(outputdir,"/TUCR_Database/",TUCRname,"/",sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/",TUCRname,"/",sep=""))
}
#if(file.exists(paste(outputdir,"/TUCR_Database/",TUCRname,"/",figureorder,"_",TUCRname,"_",disease,"_tpm_boxplot.png",sep = ""))){}else{
tpm.dotplot2 <- tpm.dotplot %>% dplyr::filter(TUCRids == TUCR)

tpm.dotplot2$IDH1status<-factor(tpm.dotplot2$IDH1status,levels=c("normal","WT","MUT"))
p<- ggplot(tpm.dotplot2, aes(x=IDH1status, y=TPM)) +
  geom_boxplot(outlier.color="white") +
  #geom_violin(trim = FALSE)+
  #geom_point(pch=21, size=1.5) +
  geom_jitter(binaxis='y', stackdir='center', stackratio=0.90, dotsize=0.30,fill="gray",width=0.2) +
  #ggtitle(paste(tpmethod," expression of ",TUCR)) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        plot.title = element_text(size = rel(2.2), hjust = 0.5, face="bold",margin=margin(0,0,0,0)),
        axis.title = element_text(size = rel(1.6), face="bold"),
        axis.text.y = element_text(size = rel(2.2)),
        axis.text.x = element_text(size = rel(2.2),angle=90,vjust = 0.5, hjust=1),
              #panel.grid = element_line(color = "lightgray",size = 0.75),
        legend.position="none",
        legend.title=element_blank(),
        legend.text=element_blank()) +
        labs(y=paste(ifelse((tpmethod=="tpm"|tpmethod=="TPM"),
                      "Transcripts per kilobase million (TPM)",
                      "Reads per kilobase million (tpm)")),
        x = "IDH1 status",title=disease) +
  stat_summary(fun.y=mean, geom="point", shape=20, size=6, color=paper_blue, fill=paper_blue)

ggsave(p,file=paste(outputdir,"/TUCR_Database/",TUCRname,"/",figureorder,"_",TUCRname,"_",disease,"_tpm_boxplot.png",sep = ""),height=7,width=5)

}

```

## Survival analysis GBM
```{r Survival_analysis_GBM}

disease <- "GBM"

normal <- "cortex"

figureorder <- 5

## read data

t_countfile <- paste("./Inputs/general_files/sequencingfiles/",disease,"/",disease,"_mergedcounts.txt",sep="")

n_countfile <- paste("./Inputs/general_files/sequencingfiles/",normal,"/",normal,"_mergedcounts.txt",sep="")

t_metadatafile <- paste("./Inputs/general_files/sequencingfiles/",disease,"/",disease,"_tcga_metadata.csv",sep="")

n_metadatafile <- paste("./Inputs/general_files/sequencingfiles/",normal,"/",normal,"_gtex_metadata.csv",sep="")

t_seqdepthfile <- paste("./Inputs/general_files/sequencingfiles/",disease,"/",disease,"_seqdepth_counts.csv",sep="")

n_seqdepthfile <- paste("./Inputs/general_files/sequencingfiles/",normal,"/",normal,"_seqdepth_counts.csv",sep="")

## Merge Data

if(!is.na(n_countfile)){
  mergedcounts <- read.table(t_countfile,header = TRUE)
  
  normalcounts <- read.table(n_countfile,header = TRUE) 
  
  mergedcounts <- mergedcounts %>% left_join(normalcounts,by=c("id")) %>%
    dplyr::select(-chrom.y,-start.y,-end.y,-strand.y,-tag.y,-annot.y,-alias.y) %>%
    distinct()
  
  metadata <- 
  read_csv(file = t_metadatafile)
  
  n_metadata <- 
  read_csv(file = n_metadatafile)
  
  rm(normalcounts)
  
  metadata <- rbind(metadata,n_metadata)
  
  rm(n_metadata)
  
  seqdepth <- read.csv(file = t_seqdepthfile)
  
  n_seqdepth <- read.csv(file = n_seqdepthfile)
  
  seqdepth <- rbind(seqdepth,n_seqdepth)
  
  rm(n_seqdepth)
  
}else{
    mergedcounts <- read.table(t_countfile,header = TRUE)

    metadata <- read.csv(file = t_metadatafile)
    
    seqdepth <- read.csv(file = t_seqdepthfile)
}

#if(!dir.exists(paste(outputdir,"/TUCR_Database/",sep=""))){
#  dir.create(paste(outputdir,"/TUCR_Database/",sep=""))
#}

#if(!dir.exists(paste(outputdir,"/TUCR_Database/SummaryTables/",sep=""))){
#  dir.create(paste(outputdir,"/TUCR_Database/SummaryTables/",sep=""))
#}

#if(!dir.exists(paste(outputdir,"/TUCR_Database/SummaryTables/",disease,sep=""))){
#  dir.create(paste(outputdir,"/TUCR_Database/SummaryTables/",disease,sep=""))
#}

if(!is.na(filterannot)){
  survcounts <- mergedcounts %>%
    filter(tag.x == filterannot & annot.x != "random")
  
}else{
  survcounts <- mergedcounts
}

posdata <- survcounts[,1:8]
survcounts <- survcounts[,9:length(colnames(survcounts))]

is.sequential <- function(x){
  all(abs(diff(x)) == 1)
} 

match_colnames <- match(as.character(colnames(survcounts)),as.character(metadata$survid))

survcounts <- as.matrix(survcounts)

n_index <- which(as.character(metadata$dex) %in% "normal")

## modifying this command to only subset with IDH status WT for GBM
#t_index <- which(as.character(metadata$dex) %in% "tumor")

t_index <- which(as.character(metadata$IDH1status) %in% "WT")

vm <- function(x){
  #x <- mergedcounts
  cond <- factor(ifelse(seq(1,dim(x)[2],1) %in% t_index, 1,  0))
  d <- model.matrix(~1+cond)
  x <- t(apply(x,1,as.numeric))
  ex <- voom(x,d,plot=F)
  return(ex$E)
}

count_vm <- vm(survcounts)

colnames(count_vm) <- metadata$id

scal <- function(x,y){
  mean_n <- rowMeans(y)  # mean of normal
  sd_n <- apply(y,1,sd)  # SD of normal
  # z score as (value - mean normal)/SD normal
  res <- matrix(nrow=nrow(x), ncol=ncol(x))
  colnames(res) <- colnames(x)
  rownames(res) <- rownames(x)
  for(i in 1:dim(x)[1]){
    for(j in 1:dim(x)[2]){
      res[i,j] <- (x[i,j]-mean_n[i])/sd_n[i]
    }
  }
  return(res)
}

z_rna <- scal(count_vm[,t_index],count_vm[,n_index])
rownames(z_rna) <- posdata[,4]

#clinical <- read.table("./Inputs/general_files/survivalfiles/GBM.clin.merged.txt",header = TRUE)
clinical <- read.table("./Inputs/general_files/survivalfiles/glioma3.clin.merged.txt",header = TRUE)

clinical$time <- as.numeric(clinical$time)

clinical <- clinical %>%
  dplyr::select("barcode"=patient,time,status)

clinical2 <- metadata %>% left_join(clinical,by = "barcode")

# Sum(clinical$patient %in% colnames(z_rna))

ind_tum <- which(unique(colnames(z_rna)) %in% clinical2$id)
ind_clin <- which(clinical2$id %in% colnames(z_rna))

out.tab <- c()
for(x in 1:nrow(count_vm)){
  ind_gene <- x
  s <- Surv(clinical$time[ind_clin],clinical$status[ind_clin])
  cx <- coxph(formula = s ~ z_rna[ind_gene,ind_tum])
  cx <- tidy(cx)
  out.tab <- rbind(out.tab,cx)
}

surv_TUCR <- cbind(posdata,out.tab)
surv_TUCR <- surv_TUCR %>% dplyr::select(-term)

write_csv(surv_TUCR,paste(outputdir,"/TUCR_Database/SummaryTables/",disease,"/",disease,"_survival_coxph_allTUCRs.csv",sep=""))


km_countdata <- z_rna
colnames(km_countdata) <- metadata$id[t_index]
posdata$median <- rowMedians(survcounts)

#km_countdata2 <- km_countdata[,complete.cases(clinical2)]

probs <- c(0.25,0.5,0.75)
q <- rowQuantiles(km_countdata, probs = probs)
posdata$n25 <- q[,1]
posdata$n75 <- q[,3]
posdata <- posdata %>%
  dplyr::select("TUCR"=alias.x,median,n25,n75)
km_TUCRs <- cbind(posdata,km_countdata) 

km_TUCRs <- km_TUCRs %>%
  gather(key = "id", value = "count",-TUCR,-median,-n75,-n25) %>%
  mutate(group = ifelse(count>=n75,"high",ifelse(count<=n25,"low",NA))) %>%
  distinct %>%
  dplyr::select(TUCR,median,id,group) %>%
  left_join(clinical2,by="id") %>%
  dplyr::filter(median != 0)

TUCRids <- as.character(posdata$TUCR)
i <- 1

ptable <- data.frame(matrix(ncol=3,nrow=0, dimnames=list(NULL, c("TUCR","pvalue","method"))))

for(i in 1:length(TUCRids)){
 print(i)
  print(TUCRids[i])
  
  skip_to_next <- FALSE
  TUCRsurv <- as.character(TUCRids[i])
  if(!dir.exists(paste(outputdir,"/TUCR_Database/",TUCRsurv,sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/",TUCRsurv,sep=""))
  } 
  #TUCRsurv<-"uc.1"
  #TUCR <- "uc.1"
  kmdata <- km_TUCRs %>%
   dplyr::filter(TUCR == TUCRsurv) %>%
   dplyr::select(TUCR,id,group,time,status) 
  fit <- tryCatch(survfit(Surv(time, status) ~ group, data = kmdata),
               error = function(e) { skip_to_next <<- TRUE})
  p <- tryCatch(ggsurvplot(fit,data=kmdata,conf.int = TRUE,pval = TRUE,risk.table = TRUE),
               error = function(e) { skip_to_next <<- TRUE})
  #p <- ggsurvplot(fit,data=kmdata,conf.int = TRUE,pval = TRUE,risk.table = TRUE)
                
  if(skip_to_next == TRUE) { 
   rbinder <- cbind(as.character(TUCRsurv),NA,NA)
    ptable[i,] <- rbinder } else{
  grid.draw.ggsurvplot <- function(x){
  survminer:::print.ggsurvplot(x, newpage = FALSE)
  }
 p <- ggsurvplot(fit,data=kmdata,conf.int = TRUE,pval = TRUE,risk.table = TRUE)
 ggsave(file=paste(outputdir,"/TUCR_Database/",TUCRsurv,"/",figureorder,"_",TUCRsurv,"_",disease,"_kpmplot.png",sep = ""), device="png", plot=p)
  p2value <- surv_pvalue(fit,  data = kmdata,method = "survdiff") %>%
   dplyr::mutate(padj = p.adjust(pval, method = "bonferroni")) %>%
   ## we are selecting three columns here and adding uc.id in next step making four columns for each uc.id 
   ## Above ptable was initiated with only three columns (TUCR,pvalue,method) 
   ## Warning in `[<-.data.frame`(`*tmp*`, i, , value = list(`as.character(TUCRsurv)` = "uc.272",  :
   ## provided 4 variables to replace 3 variables
   ## modifying below line to select only two columns (pval,method) matching above ptable initiation and if condition.   
   #dplyr::select(method,pval,padj)
    dplyr::select(pval,method)
  rbinder <- cbind(as.character(TUCRsurv),p2value)
  ptable[i,] <- rbinder
   } 

}

write_csv(ptable,paste(outputdir,"/TUCR_Database/SummaryTables/",disease,"/",disease,"_survival_kpm_allTUCRs.csv",sep=""))

```

## Survival analysis LGG, LGG_WT and LGG_MUT 

```{r Figure1ef_LGG}

disease <- "LGG"

normal <- "cortex"

figureorder <- 6

## read data

t_countfile <- paste("./Inputs/general_files/sequencingfiles/",disease,"/",disease,"_mergedcounts.txt",sep="")

n_countfile <- paste("./Inputs/general_files/sequencingfiles/",normal,"/",normal,"_mergedcounts.txt",sep="")

t_metadatafile <- paste("./Inputs/general_files/sequencingfiles/",disease,"/",disease,"_tcga_metadata.csv",sep="")

n_metadatafile <- paste("./Inputs/general_files/sequencingfiles/",normal,"/",normal,"_gtex_metadata.csv",sep="")

t_seqdepthfile <- paste("./Inputs/general_files/sequencingfiles/",disease,"/",disease,"_seqdepth_counts.csv",sep="")

n_seqdepthfile <- paste("./Inputs/general_files/sequencingfiles/",normal,"/",normal,"_seqdepth_counts.csv",sep="")

## Merge Data

if(!is.na(n_countfile)){
  mergedcounts <- read.table(t_countfile,header = TRUE)
  
  normalcounts <- read.table(n_countfile,header = TRUE) 
  
  mergedcounts <- mergedcounts %>% left_join(normalcounts,by=c("id")) %>%
    dplyr::select(-chrom.y,-start.y,-end.y,-strand.y,-tag.y,-annot.y,-alias.y) %>%
    distinct()
  
  metadata <- 
  read_csv(file = t_metadatafile)
  
  n_metadata <- 
  read_csv(file = n_metadatafile)
  
  rm(normalcounts)
  
  metadata <- rbind(metadata,n_metadata)
  
  rm(n_metadata)
  
  seqdepth <- read.csv(file = t_seqdepthfile)
  
  n_seqdepth <- read.csv(file = n_seqdepthfile)
  
  seqdepth <- rbind(seqdepth,n_seqdepth)
  
  rm(n_seqdepth)
  
}else{
    mergedcounts <- read.table(t_countfile,header = TRUE)

    metadata <- read.csv(file = t_metadatafile)
    
    seqdepth <- read.csv(file = t_seqdepthfile)
}

if(!dir.exists(paste(outputdir,"/TUCR_Database/",sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/",sep=""))
}

if(!dir.exists(paste(outputdir,"/TUCR_Database/SummaryTables/",sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/SummaryTables/",sep=""))
}

if(!dir.exists(paste(outputdir,"/TUCR_Database/SummaryTables/",disease,sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/SummaryTables/",disease,sep=""))
}

if(!is.na(filterannot)){
  survcounts <- mergedcounts %>%
    #filter(tag.x == filterannot & annot.x != "random" | id == "CASZ1___chr1:10636602-10796676:-")
    filter(tag.x == filterannot & annot.x != "random")
  
}else{
  survcounts <- mergedcounts
}

posdata <- survcounts[,1:8]
survcounts <- survcounts[,9:length(colnames(survcounts))]

is.sequential <- function(x){
  all(abs(diff(x)) == 1)
} 

match_colnames <- match(as.character(colnames(survcounts)),as.character(metadata$survid))

survcounts <- as.matrix(survcounts)

n_index <- which(as.character(metadata$dex) %in% "normal")
t_index <- which(as.character(metadata$dex) %in% "tumor")

vm <- function(x){
  #x <- mergedcounts
  cond <- factor(ifelse(seq(1,dim(x)[2],1) %in% t_index, 1,  0))
  d <- model.matrix(~1+cond)
  x <- t(apply(x,1,as.numeric))
  ex <- voom(x,d,plot=F)
  return(ex$E)
}

count_vm <- vm(survcounts)

colnames(count_vm) <- metadata$id

scal <- function(x,y){
  mean_n <- rowMeans(y)  # mean of normal
  sd_n <- apply(y,1,sd)  # SD of normal
  # z score as (value - mean normal)/SD normal
  res <- matrix(nrow=nrow(x), ncol=ncol(x))
  colnames(res) <- colnames(x)
  rownames(res) <- rownames(x)
  for(i in 1:dim(x)[1]){
    for(j in 1:dim(x)[2]){
      res[i,j] <- (x[i,j]-mean_n[i])/sd_n[i]
    }
  }
  return(res)
}

z_rna <- scal(count_vm[,t_index],count_vm[,n_index])
rownames(z_rna) <- posdata[,4]

clinical <- read.table("./Inputs/general_files/survivalfiles/glioma3.clin.merged.txt",header = TRUE)

clinical$time <- as.numeric(clinical$time)

clinical <- clinical %>%
  dplyr::select("barcode"=patient,time,status)

clinical2 <- metadata %>% left_join(clinical,by = "barcode")

## 
clinical2_mut<-clinical2[clinical2$IDH1status=="MUT",]
z_rna_mut<-z_rna[,clinical2_mut$id]
clinical2_wt<-clinical2[clinical2$IDH1status=="WT",]
z_rna_wt<-z_rna[,clinical2_wt$id]
# Sum(clinical$patient %in% colnames(z_rna))

ind_tum <- which(unique(colnames(z_rna)) %in% clinical2$id)

## to get index of tumor samples in clinical2 dataset and it has IDH1 status
ind_clin <- which(clinical2$id %in% colnames(z_rna))

## this is for LGG wt type 
out.tab <- c()
for(x in 1:nrow(count_vm)){
  ind_gene <- x
  s <- Surv(clinical$time[ind_clin],clinical$status[ind_clin])
  cx <- coxph(formula = s ~ z_rna[ind_gene,ind_tum])
  cx <- tidy(cx)
  out.tab <- rbind(out.tab,cx)
}

out.tab$estimate <- -out.tab$estimate
surv_TUCR <- cbind(posdata,out.tab)
surv_TUCR <- surv_TUCR %>% dplyr::select(-term)

write_csv(surv_TUCR,paste(outputdir,"/TUCR_Database/SummaryTables/",disease,"/",disease,"_survival_coxph_allTUCRs.csv",sep=""))

km_countdata <- z_rna
#colnames(km_countdata) <- metadata$id[t_index]

## rowmedians considering all LGG samples count matrix
## copying posdata in to posdata for ptable as in this we are selecting few columns and we need initial posdata dataset for LGG mut cox analysis
posdata1<-posdata

posdata1$median <- rowMedians(survcounts)

#km_countdata2 <- km_countdata[,complete.cases(clinical2)]

probs <- c(0.25,0.5,0.75)
q <- rowQuantiles(km_countdata, probs = probs)
posdata1$n25 <- q[,1]
posdata1$n75 <- q[,3]
posdata1 <- posdata1 %>%
  dplyr::select("TUCR"=alias.x,median,n25,n75)
km_TUCRs <- cbind(posdata1,km_countdata) 

km_TUCRs <- km_TUCRs %>%
  gather(key = "id", value = "count",-TUCR,-median,-n75,-n25) %>%
  mutate(group = ifelse(count>=n75,"high",ifelse(count<=n25,"low",NA))) %>%
  distinct %>%
  dplyr::select(TUCR,median,id,group) %>%
  left_join(clinical2,by="id") %>%
  dplyr::filter(median != 0)

TUCRids <- as.character(posdata1$TUCR)
i <- 1

ptable <- data.frame(matrix(ncol=3,nrow=0, dimnames=list(NULL, c("TUCR","pvalue","method"))))

for(i in 1:length(TUCRids)){
  print(i)
  print(TUCRids[i])
  
  skip_to_next <- FALSE
  TUCRsurv <- as.character(TUCRids[i])
  if(!dir.exists(paste(outputdir,"/TUCR_Database/",TUCRsurv,sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/",TUCRsurv,sep=""))
  } 
  #TUCRsurv<-"uc.1"
  #TUCR <- "uc.1"
  kmdata <- km_TUCRs %>%
   dplyr::filter(TUCR == TUCRsurv) %>%
   dplyr::select(TUCR,id,group,time,status) 
  fit <- tryCatch(survfit(Surv(time, status) ~ group, data = kmdata),
               error = function(e) { skip_to_next <<- TRUE})
  p <- tryCatch(ggsurvplot(fit,data=kmdata,conf.int = TRUE,pval = TRUE,risk.table = TRUE),
               error = function(e) { skip_to_next <<- TRUE})
  #p <- ggsurvplot(fit,data=kmdata,conf.int = TRUE,pval = TRUE,risk.table = TRUE)
                
  if(skip_to_next == TRUE) { 
   rbinder <- cbind(as.character(TUCRsurv),NA,NA)
    ptable[i,] <- rbinder } else{
  grid.draw.ggsurvplot <- function(x){
  survminer:::print.ggsurvplot(x, newpage = FALSE)
  }
 p <- ggsurvplot(fit,data=kmdata,conf.int = TRUE,pval = TRUE,risk.table = TRUE)
 ggsave(file=paste(outputdir,"/TUCR_Database/",TUCRsurv,"/",figureorder,"_",TUCRsurv,"_",disease,"_kpmplot.png",sep = ""), device="png", plot=p)
 
  p2value <- surv_pvalue(fit,  data = kmdata,method = "survdiff") %>%
   dplyr::mutate(padj = p.adjust(pval, method = "bonferroni")) %>%
   ## we are selecting three columns here and adding uc.id in next step making four columns for each uc.id 
   ## Above ptable was initiated with only three columns (TUCR,pvalue,method) 
   ## Warning in `[<-.data.frame`(`*tmp*`, i, , value = list(`as.character(TUCRsurv)` = "uc.272",  :
   ## provided 4 variables to replace 3 variables
   ## modifying below line to select only two columns (pval,method) matching above ptable initiation and if condition.   
   #dplyr::select(method,pval,padj)
    dplyr::select(pval,method)
  rbinder <- cbind(as.character(TUCRsurv),p2value)
  ptable[i,] <- rbinder
   } 

}

write_csv(ptable,paste(outputdir,"/TUCR_Database/SummaryTables/",disease,"/",disease,"_survival_kpm_allTUCRs.csv",sep=""))

### LGG-WT

disease <- "LGG_WT"

figureorder <- 7

out.tab <- c()
for(x in 1:nrow(count_vm)){
   ind_gene <- x
   s <- Surv(clinical2_wt$time,clinical2_wt$status)
  cx <- coxph(formula = s ~ z_rna_wt[ind_gene,])
  cx <- tidy(cx)
  out.tab <- rbind(out.tab,cx)
}
out.tab$estimate <- -out.tab$estimate

surv_TUCR <- cbind(posdata,out.tab)
surv_TUCR <- surv_TUCR %>% dplyr::select(-term)

write_csv(surv_TUCR,paste(outputdir,"/TUCR_Database/SummaryTables/",disease,"/",disease,"_survival_coxph_allTUCRs.csv",sep=""))

km_countdata <- z_rna_wt
#colnames(km_countdata) <- metadata$id[t_index]

## rowmedians considering all LGG samples count matrix
## copying posdata in to posdata for ptable as in this we are selecting few columns and we need initial posdata dataset for LGG mut cox analysis
posdata1<-posdata

posdata1$median <- rowMedians(survcounts)

#km_countdata2 <- km_countdata[,complete.cases(clinical2)]

probs <- c(0.25,0.5,0.75)
q <- rowQuantiles(km_countdata, probs = probs)
posdata1$n25 <- q[,1]
posdata1$n75 <- q[,3]
posdata1 <- posdata1 %>%
  dplyr::select("TUCR"=alias.x,median,n25,n75)
km_TUCRs <- cbind(posdata1,km_countdata) 

km_TUCRs <- km_TUCRs %>%
  gather(key = "id", value = "count",-TUCR,-median,-n75,-n25) %>%
  mutate(group = ifelse(count>=n75,"high",ifelse(count<=n25,"low",NA))) %>%
  distinct %>%
  dplyr::select(TUCR,median,id,group) %>%
  left_join(clinical2_wt,by="id") %>%
  dplyr::filter(median != 0)

TUCRids <- as.character(posdata1$TUCR)
i <- 1

ptable <- data.frame(matrix(ncol=3,nrow=0, dimnames=list(NULL, c("TUCR","pvalue","method"))))

for(i in 1:length(TUCRids)){
  print(i)
  print(TUCRids[i])
  
  skip_to_next <- FALSE
  TUCRsurv <- as.character(TUCRids[i])
  if(!dir.exists(paste(outputdir,"/TUCR_Database/",TUCRsurv,sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/",TUCRsurv,sep=""))
  } 
  #TUCRsurv<-"uc.1"
  #TUCR <- "uc.1"
  kmdata <- km_TUCRs %>%
   dplyr::filter(TUCR == TUCRsurv) %>%
   dplyr::select(TUCR,id,group,time,status) 
  fit <- tryCatch(survfit(Surv(time, status) ~ group, data = kmdata),
               error = function(e) { skip_to_next <<- TRUE})
  p <- tryCatch(ggsurvplot(fit,data=kmdata,conf.int = TRUE,pval = TRUE,risk.table = TRUE),
               error = function(e) { skip_to_next <<- TRUE})
  #p <- ggsurvplot(fit,data=kmdata,conf.int = TRUE,pval = TRUE,risk.table = TRUE)
                
  if(skip_to_next == TRUE) { 
   rbinder <- cbind(as.character(TUCRsurv),NA,NA)
    ptable[i,] <- rbinder } else{
  grid.draw.ggsurvplot <- function(x){
  survminer:::print.ggsurvplot(x, newpage = FALSE)
  }
 p <- ggsurvplot(fit,data=kmdata,conf.int = TRUE,pval = TRUE,risk.table = TRUE)
 ggsave(file=paste(outputdir,"/TUCR_Database/",TUCRsurv,"/",figureorder,"_",TUCRsurv,"_",disease,"_kpmplot.png",sep = ""), device="png", plot=p)
 
  if(TUCRsurv == "uc.75"){
    ggsave(file=paste(outputdir,"/Figure1/figure1e.png",sep = ""), device="png", plot=p)
 }
 
 if(TUCRsurv == "uc.132"){
    ggsave(file=paste(outputdir,"/Figure1/figure1f.png",sep = ""), device="png", plot=p)
 }
 
 if(!dir.exists(paste(outputdir,"/Figure6_Supplementary/",sep=""))){
  dir.create(paste(outputdir,"/Figure6_Supplementary/",sep=""))
 }
 
 if(!dir.exists(paste(outputdir,"/Figure7_Supplementary/",sep=""))){
  dir.create(paste(outputdir,"/Figure7_Supplementary/",sep=""))
}
 
 if(TUCRsurv == "uc.2"){
    ggsave(file=paste(outputdir,"/Figure6_supplementary/supplementary_figure6g.png",sep = ""), device="png", plot=p)
 }
 
 if(TUCRsurv == "uc.15"){
    ggsave(file=paste(outputdir,"/Figure7_supplementary/supplementary_figure7g.png",sep = ""), device="png", plot=p)
 }

  p2value <- surv_pvalue(fit,  data = kmdata,method = "survdiff") %>%
   dplyr::mutate(padj = p.adjust(pval, method = "bonferroni")) %>%
   ## we are selecting three columns here and adding uc.id in next step making four columns for each uc.id 
   ## Above ptable was initiated with only three columns (TUCR,pvalue,method) 
   ## Warning in `[<-.data.frame`(`*tmp*`, i, , value = list(`as.character(TUCRsurv)` = "uc.272",  :
   ## provided 4 variables to replace 3 variables
   ## modifying below line to select only two columns (pval,method) matching above ptable initiation and if condition.   
   #dplyr::select(method,pval,padj)
    dplyr::select(pval,method)
  rbinder <- cbind(as.character(TUCRsurv),p2value)
  ptable[i,] <- rbinder
   } 

}

write_csv(ptable,paste(outputdir,"/TUCR_Database/SummaryTables/",disease,"/",disease,"_survival_kpm_allTUCRs.csv",sep=""))
## this is for LGG mut type
disease<-"LGG_MUT"

figureorder <- 8

out.tab <- c()
for(x in 1:nrow(count_vm)){
   ind_gene <- x
   s <- Surv(clinical2_mut$time,clinical2_mut$status)
  cx <- coxph(formula = s ~ z_rna_mut[ind_gene,])
  cx <- tidy(cx)
  out.tab <- rbind(out.tab,cx)
}
out.tab$estimate <- -out.tab$estimate

surv_TUCR <- cbind(posdata,out.tab)
surv_TUCR <- surv_TUCR %>% dplyr::select(-term)

write_csv(surv_TUCR,paste(outputdir,"/TUCR_Database/SummaryTables/",disease,"/",disease,"_survival_coxph_allTUCRs.csv",sep=""))

km_countdata <- z_rna_mut
#colnames(km_countdata) <- metadata$id[t_index]
posdata$median <- rowMedians(survcounts)

#km_countdata2 <- km_countdata[,complete.cases(clinical2)]

probs <- c(0.25,0.5,0.75)
q <- rowQuantiles(km_countdata, probs = probs)
posdata$n25 <- q[,1]
posdata$n75 <- q[,3]
posdata <- posdata %>%
  dplyr::select("TUCR"=alias.x,median,n25,n75)
km_TUCRs <- cbind(posdata,km_countdata) 

km_TUCRs <- km_TUCRs %>%
  gather(key = "id", value = "count",-TUCR,-median,-n75,-n25) %>%
  mutate(group = ifelse(count>=n75,"high",ifelse(count<=n25,"low",NA))) %>%
  distinct %>%
  dplyr::select(TUCR,median,id,group) %>%
  left_join(clinical2_mut,by="id") %>%
  dplyr::filter(median != 0)

TUCRids <- as.character(posdata$TUCR)
i <- 1

ptable <- data.frame(matrix(ncol=3,nrow=0, dimnames=list(NULL, c("TUCR","pvalue","method"))))

for(i in 1:length(TUCRids)){
  print(i)
  print(TUCRids[i])
  
  skip_to_next <- FALSE
  TUCRsurv <- as.character(TUCRids[i])
  if(!dir.exists(paste(outputdir,"/TUCR_Database/",TUCRsurv,sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/",TUCRsurv,sep=""))
  } 
  #TUCRsurv<-"uc.1"
  #TUCR <- "uc.1"
  kmdata <- km_TUCRs %>%
   dplyr::filter(TUCR == TUCRsurv) %>%
   dplyr::select(TUCR,id,group,time,status) 
  fit <- tryCatch(survfit(Surv(time, status) ~ group, data = kmdata),
               error = function(e) { skip_to_next <<- TRUE})
  p <- tryCatch(ggsurvplot(fit,data=kmdata,conf.int = TRUE,pval = TRUE,risk.table = TRUE),
               error = function(e) { skip_to_next <<- TRUE})
  #p <- ggsurvplot(fit,data=kmdata,conf.int = TRUE,pval = TRUE,risk.table = TRUE)
                
  if(skip_to_next == TRUE) { 
   rbinder <- cbind(as.character(TUCRsurv),NA,NA)
    ptable[i,] <- rbinder } else{
  grid.draw.ggsurvplot <- function(x){
  survminer:::print.ggsurvplot(x, newpage = FALSE)
  }

 p <- ggsurvplot(fit,data=kmdata,conf.int = TRUE,pval = TRUE,risk.table = TRUE)
 ggsave(file=paste(outputdir,"/TUCR_Database/",TUCRsurv,"/",figureorder,"_",TUCRsurv,"_",disease,"_kpmplot.png",sep = ""), device="png", plot=p)
 
  if(!dir.exists(paste(outputdir,"/Figure6_Supplementary/",sep=""))){
  dir.create(paste(outputdir,"/Figure6_Supplementary/",sep=""))
 }
 
 if(!dir.exists(paste(outputdir,"/Figure7_Supplementary/",sep=""))){
  dir.create(paste(outputdir,"/Figure7_Supplementary/",sep=""))
}
 
 if(TUCRsurv == "uc.2"){
    ggsave(file=paste(outputdir,"/Figure6_supplementary/supplementary_figure6h.png",sep = ""), device="png", plot=p)
 }
 
 if(TUCRsurv == "uc.15"){
    ggsave(file=paste(outputdir,"/Figure7_supplementary/supplementary_figure7h.png",sep = ""), device="png", plot=p)
 }
 
  p2value <- surv_pvalue(fit,  data = kmdata,method = "survdiff") %>%
   dplyr::mutate(padj = p.adjust(pval, method = "bonferroni")) %>%
   ## we are selecting three columns here and adding uc.id in next step making four columns for each uc.id 
   ## Above ptable was initiated with only three columns (TUCR,pvalue,method) 
   ## Warning in `[<-.data.frame`(`*tmp*`, i, , value = list(`as.character(TUCRsurv)` = "uc.272",  :
   ## provided 4 variables to replace 3 variables
   ## modifying below line to select only two columns (pval,method) matching above ptable initiation and if condition.   
   #dplyr::select(method,pval,padj)
    dplyr::select(pval,method)
  rbinder <- cbind(as.character(TUCRsurv),p2value)
  ptable[i,] <- rbinder
    } 

}

write_csv(ptable,paste(outputdir,"/TUCR_Database/SummaryTables/",disease,"/",disease,"_survival_kpm_allTUCRs.csv",sep=""))

```


## Code for generating WGCNA module data and saving as allprelims.Rdata 
```{r Supplementary_TUCR_database_relatingmodules_1,eval=FALSE}

# Load the WGCNA package
library(WGCNA)
# The following setting is important, do not omit.
options(stringsAsFactors = FALSE)
# Load the expression and trait data saved in the first part
lnames = load(file = "./Inputs/general_files/wgcnafiles/TUCR-01-dataInput.RData")
#The variable lnames contains the names of loaded variables.
lnames
# Load network data saved in the second part.
lnames = load(file = "./Inputs/general_files/wgcnafiles/TUCR-02-networkConstruction-auto.RData")
lnames

```
## filter out modules that are particularly large. 

```{r Supplementary_TUCR_database_relatingmodules_2,fig.width = 3, fig.height = 7,eval=FALSE}

# Define numbers of genes and samples
nGenes = ncol(datExpr)
nSamples = nrow(datExpr)
# Recalculate MEs with color labels
MEs0 = moduleEigengenes(datExpr, moduleColors)$eigengenes

datExpr2 = as.data.frame(datExpr)
MEs = orderMEs(MEs0)
datTraits2 <- as.data.frame(datTraits2)
moduleTraitCor = cor(MEs, datTraits2, use = "p")
moduleTraitPvalue = corPvalueStudent(moduleTraitCor, nSamples)

```

```{r Supplementary_TUCR_database_relatingmodules_3,eval=FALSE}

geneModuleMembership = as.data.frame(cor(datExpr, MEs, use = "p"))
MMPvalue = as.data.frame(corPvalueStudent(as.matrix(geneModuleMembership), nSamples))

allmodules <- as.data.frame(t(MMPvalue))
#allmodules : 51 *42644
allmodules2 <- allmodules %>%
  dplyr::mutate(Module = row.names(allmodules)) %>%
  gather(key = "Gene", value = "pvalue",-Module) %>%
  group_by(Gene) %>%
  mutate(maxmodule = min(pvalue,na.rm = TRUE)) %>%
  filter(pvalue == maxmodule) %>%
  group_by(Module) %>%
  dplyr::summarize(n = n()) 

allmodules3 <- allmodules2 %>%
  mutate(q1 = quantile(allmodules2$n,0.25),q3 = quantile(allmodules2$n,0.75),q1minus = q1 - 1.5*(q3-q1),q3plus = q3 + 1.5*(q3-q1),outliercheck = ifelse(n >= q3plus | n <= q1minus,TRUE,FALSE)) 
#%>%  filter(outliercheck == FALSE)

#repeat{
  
n_count <- length(allmodules3$n)

allmodules3 <- allmodules3 %>%
  mutate(q1 = quantile(allmodules3$n,0.25),q3 = quantile(allmodules3$n,0.75),q1minus = q1 - 1.5*(q3-q1),q3plus = q3 + 1.5*(q3-q1),outliercheck = ifelse(n >= q3plus | n <= q1minus,TRUE,FALSE)) 
#%>% filter(outliercheck == FALSE)

#if(n_count == length(allmodules3$n)) break;

#  }

allmodules_check <- as.data.frame(as.character(allmodules3$Module)) %>%
  dplyr::mutate(checker = TRUE)

colnames(allmodules_check) <- c("Module","checker")

boxplot(allmodules3$n,
  ylab = "n"
)

moduleTraitCor2 <- as.data.frame(moduleTraitCor) %>%
  mutate(Module = row.names(moduleTraitCor)) %>%
  left_join(allmodules_check,by = "Module") %>%
  filter(checker == TRUE)

datTraits <- datTraits2

geneModuleMembership = as.data.frame(cor(datExpr, MEs, use = "p"))

match_modules <- match(as.character(allmodules_check$Module),colnames(geneModuleMembership))

geneModuleMembership2 <- geneModuleMembership[,match_modules]

modNames = substring(names(geneModuleMembership2), 3)

MMPvalue = as.data.frame(corPvalueStudent(as.matrix(geneModuleMembership), nSamples))

match_modules <- match(as.character(allmodules_check$Module),colnames(MMPvalue))

MMPvalue2 = MMPvalue[,match_modules]

names(geneModuleMembership2) = paste("MM", modNames, sep="")
names(MMPvalue2) = paste("p.MM", modNames, sep="")

# Save.image(file="./Inputs/general_files/wgcnafiles/allprelims.Rdata")

```

```{r}
load(file="./Inputs/general_files/wgcnafiles/allprelims.Rdata")

datTraits2 <- datTraits2 %>%
  dplyr::select(-disease)

datTraits <- as.data.frame(t(datTraits2)) %>%
  mutate(rownames = row.names(t(datTraits2))) %>%
  # Filter(rownames == trait_id) %>%
  dplyr::select(-rownames) %>%
  t()

hc.Traits <- hclust(dist(t(datTraits2)))

clust_order_traits <- hc.Traits$order

clust_positions <- as.data.frame(cbind(as.character(colnames(datTraits)[clust_order_traits]),as.numeric(clust_order_traits)))

colnames(clust_positions) <- c("trait","clust_order")

geneTraitSignificance <- as.data.frame(cor(datExpr,datTraits2, use = "p")) %>%
  dplyr::select(-dex2,-p53status2)

GSPvalue = as.data.frame(corPvalueStudent(as.matrix(geneTraitSignificance), nSamples))

#names(geneTraitSignificance) = paste("GS.", names(weight), sep="")
#names(GSPvalue) = paste("p.GS.", names(weight), sep="")

moduleTraitCor_trait_id <- as.data.frame(moduleTraitCor2) %>%
  mutate(modules = str_remove(Module,"ME")) %>%
  gather(key = "trait", value = "cor",-modules,-Module,-checker,-p53status2,-dex2) %>%
  # Filter(is.numeric(cor)) %>%
  # Filter(trait == trait_id) %>%
  dplyr::group_by(trait) %>%
  arrange(desc(cor)) %>%
  ungroup() %>%
  dplyr::group_by(modules) %>%
  dplyr::mutate(sumnumber = sum(cor,na.rm=T),
         n = n(),
         weight = sumnumber/n) %>%
  ungroup() %>%
  arrange(desc(weight))

traitpositions <- moduleTraitCor_trait_id %>%
  dplyr::select(modules) %>%
  distinct() %>%
  dplyr::mutate(position = row_number())

moduleTraitCor_trait_id <- moduleTraitCor_trait_id %>%
  left_join(traitpositions,by="modules") %>%
  left_join(clust_positions,by="trait") 

moduleTraitCor_trait_id <- moduleTraitCor_trait_id %>% 
  mutate(clust_position_order = as.numeric(moduleTraitCor_trait_id$clust_order))

moduleTraitCor_trait_id$position_label<-paste0("module",moduleTraitCor_trait_id$position,"")
```

```{r}

if(!dir.exists(paste(outputdir,"/TUCR_Database/",sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/",sep=""))
}

if(!dir.exists(paste(outputdir,"/TUCR_Database/SummaryTables/",sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/SummaryTables/",sep=""))
}

if(!dir.exists(paste(outputdir,"/TUCR_Database/SummaryTables/WGCNA/",sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/SummaryTables/WGCNA/",sep=""))
}

#####GO-TERM ANALYSIS

if (!requireNamespace("BiocManager", quietly = TRUE)) install.packages("BiocManager")

if (!require('GO.db')) BiocManager::install('GO.db')
library(GO.db)

#if (!require('AnnotationDBI')) BiocManager::install('AnnotationDBI')
#library(AnnotationDBI)

if (!require('org.Hs.eg.db')) BiocManager::install('org.Hs.eg.db')
library(org.Hs.eg.db)

if (!require('limma')) BiocManager::install('limma')
library(limma)

i <- 1

genelist <- geneTraitSignificance %>%
  mutate(genenames = row.names(geneTraitSignificance))

for(i in 1:length(unique(moduleTraitCor_trait_id$modules))){
  
  print(i)
  print(unique(moduleTraitCor_trait_id$modules)[i])
  
  module <- unique(moduleTraitCor_trait_id$modules)[i]
  module_label<-unique(moduleTraitCor_trait_id$position_label)[i]
  #module <- "yellowgreen"
  column = match(module, modNames);
  moduleGenes = moduleColors==module;
  
  genelist2 <- as.data.frame(genelist[moduleGenes,])
  
  genelist2 <- genelist2 %>%
    separate(genenames,into=c("Alias","kibble"),sep="___")
 
  symbols <- as.character(genelist2$Alias)
  
  EntrezIDs <- mapIds(org.Hs.eg.db, symbols, 'ENTREZID', 'SYMBOL')
  allgenes <- cbind(symbols,EntrezIDs)
  allgenes <- allgenes[complete.cases(allgenes),]
  
  g <- goana(EntrezIDs)
  
  g_bp <- g %>%
    filter(Ont == "BP")
  topGO_bp <- topGO(g_bp) %>%
    mutate(log10_p = -log10(P.DE),module=module,color="red") %>%
    arrange(desc(log10_p))
  
  g_mf <- g %>%
    filter(Ont == "MF")
  topGO_mf <- topGO(g_mf) %>%
    mutate(log10_p = -log10(P.DE),module=module,color="blue") %>%
    arrange(desc(log10_p))
  
  topGO_all <- rbind(topGO_bp,topGO_mf) %>%
                       arrange(as.numeric(log10_p)) %>%
                       dplyr::mutate(roworder = row_number()) %>%
                       mutate(newTerm = substr(Term,1,80))
  
  p <- ggplot(topGO_all,aes(x=reorder(newTerm,roworder),y=as.numeric(log10_p),fill=module,color=color)) +
    geom_bar(stat="identity") + coord_flip() + scale_fill_identity() + scale_color_identity() + facet_wrap(~Ont,scales="free",ncol=1) + 
    ggtitle(module_label) +
    labs(x="Go Term", y = "-log10(p-value)") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        plot.title = element_text(size = rel(2.2), hjust = 0.5, face="bold",margin=margin(0,0,0,0)),
        axis.title = element_text(size = rel(1.8), face="bold"),
        axis.text.y = element_text(size = rel(1.4), face="bold"),
        axis.text.x = element_text(size = rel(1.4), face="bold",angle=0,vjust = 0.5, hjust=1),
              #panel.grid = element_line(color = "lightgray",size = 0.75),
        legend.position="none",
        legend.title=element_blank(),
        legend.text=element_blank(),
        strip.text.x = element_text(size = rel(2.2)))
  p
  
ggsave(plot = print(p),paste(outputdir,"/TUCR_Database/SummaryTables/WGCNA/",module_label,"_all_bar.png",sep=""),height=8,width=16)

}
```

## Trait Heatmaps
## TUCR_database
```{r}
####Trait Heatmaps

figureorder <- 9

#moduleTraitCor2 <- moduleTraitCor2 %>%
#  dplyr::select(-disease)

for(h in 2:482){
skip_to_next <<- FALSE
print(h)
trait_id <- colnames(moduleTraitCor2)[h]
#trait_id <-"uc.15"

print(trait_id)

if(!dir.exists(paste(outputdir,"/TUCR_Database/",trait_id,sep=""))){
  dir.create(paste(outputdir,"/TUCR_Database/",trait_id,sep=""))
}

datTraits <- as.data.frame(t(datTraits2)) %>%
  mutate(rownames = row.names(t(datTraits2))) %>%
  filter(rownames == trait_id) %>%
  dplyr::select(-rownames) %>%
  t()

geneTraitSignificance = as.data.frame(cor(datExpr,datTraits, use = "p"))

GSPvalue = as.data.frame(corPvalueStudent(as.matrix(geneTraitSignificance), nSamples))

#names(geneTraitSignificance) = paste("GS.", names(weight), sep="")
#names(GSPvalue) = paste("p.GS.", names(weight), sep="")

moduleTraitCor_trait_id <- as.data.frame(moduleTraitCor2) %>%
  dplyr::mutate(modules = str_remove(Module,"ME")) %>%
  gather(key = "trait", value = "cor",-modules) %>%
  dplyr::filter(trait == trait_id) %>%
  dplyr::arrange(cor) %>%
  dplyr::mutate(position = row_number())

traitmodules <- geneModuleMembership2 %>%
  dplyr::mutate(rownamer = row.names(geneModuleMembership2)) %>%
  separate(rownamer,into=c("rownamer","kibble"),sep="___") %>%
  dplyr::select(-kibble) %>%
  dplyr::filter(rownamer==trait_id)

traitmodules <- t(traitmodules)

traitmodules <- as.data.frame(cbind(row.names(traitmodules),traitmodules))

colnames(traitmodules) <- c("Module","ModuleMembership")

traitpvalues <- MMPvalue2 %>%
  dplyr::mutate(rownamer = row.names(MMPvalue2)) %>%
  separate(rownamer,into=c("rownamer","kibble"),sep="___") %>%
  dplyr::select(-kibble) %>%
  dplyr::filter(rownamer==trait_id)

traitpvalues <- t(traitpvalues)

traitpvalues <- as.data.frame(cbind(paste("MM",str_remove(row.names(traitpvalues),"p.MM"),sep=""),traitpvalues))

colnames(traitpvalues) <- c("Module","MMpvalue")
traitmodules <- traitmodules %>%
  left_join(allmodules_check, by= "Module") %>%
  left_join(traitpvalues,"Module") %>%
  # Filter(checker == TRUE) %>%
  dplyr::mutate(moduleColors = str_remove(Module,"MM")) %>%
  dplyr::filter(moduleColors != "rownamer")

df_correlations <- data.frame(matrix(ncol=2,nrow=0, dimnames=list(NULL, c("module","cor"))))

i <- 1

for(i in 1:length(unique(traitmodules$moduleColors))){

module = as.character(unique(traitmodules$moduleColors)[i])
#module = "red"
column = match(module, modNames)
moduleGenes = traitmodules$moduleColors==module;
correlation <- cor(abs(geneModuleMembership[moduleGenes, column]),
                   abs(geneTraitSignificance[moduleGenes, 1]))

rbinder <- c(module,correlation)
df_correlations <- rbind(df_correlations,rbinder)


}

colnames(df_correlations) <- c("module","cor") 

df_correlations <- as.data.frame(df_correlations) %>%
  mutate(Module = paste("MM",module,sep=""))

traitmodules2 <- traitmodules %>%
  left_join(df_correlations,by = "Module") %>%
  dplyr::select(module,cor,ModuleMembership,MMpvalue) %>%
  dplyr::mutate(RankModule = percent_rank(1-as.numeric(ModuleMembership)),Rankcor = percent_rank(cor),MMpvalue2 = as.numeric(MMpvalue)) %>%
  dplyr::group_by(module) %>%
  dplyr::mutate(totalscore = sum(as.numeric(RankModule),as.numeric(Rankcor),na.rm=TRUE)) %>%
  dplyr::ungroup() %>%
  dplyr::arrange(as.numeric(cor)) %>%
  dplyr::mutate(position = row_number(),cor = ifelse(MMpvalue2 >= 0.05,NA,cor))
 
#to add module names to module colors 
traitmodules2$position_label<-paste0("module",traitmodules2$position,"")

y_labels <- traitmodules2 %>%
  dplyr::distinct(module, position_label) %>%
  tibble::deframe()

p <- ggplot(
  data = traitmodules2,
  mapping = aes(
    x = as.character(trait_id),
    y = reorder(module, position),
    fill = as.numeric(cor)
  )
) +
  geom_tile() +

  scale_fill_gradient2(
    low = paper_blue,
    mid = "white",
    high = paper_red2,
    midpoint = 0
  ) +

  # Add position_label as real y-axis labels
  scale_y_discrete(labels = y_labels) +

  ylab("modules") +
  xlab(trait_id) +
  labs(fill = "cor") +

  theme(
    panel.grid.major = element_blank(), 
    panel.grid.minor = element_blank(),
    panel.background = element_blank(), 
    axis.line = element_line(colour = "black"),

    plot.title = element_text(
      size = rel(2.2),
      hjust = 0.5,
      face = "bold",
      margin = margin(0,0,0,0)
    ),

    axis.title = element_text(
      size = rel(1.8),
      face = "bold"
    ),

    # position_label rendered as real axis text
    axis.text.y = element_text(
      size = 8,
      hjust = 1
    ),

    axis.text.x = element_blank(),

    legend.position = "right",
    legend.title = element_text(
      size = rel(2.5),
      face = "bold"
    ),
    legend.text = element_text(
      size = rel(2.0),
      face = "bold"
    ),

    plot.margin = unit(c(0, 0, 0, 0.2), "cm")
  ) +

  # Existing colored squares, placed left of the axis text
  annotate(
    geom = "point",
    color = as.character(traitmodules2$module),
    y = traitmodules2$position,
    x = 0.5,
    shape = 15,
    size = 5
  ) +

  coord_cartesian(clip = "off")

p

ggsave(p,file=paste(outputdir,"/TUCR_Database/",trait_id,"/",figureorder,"_",trait_id,"_wgcna_modulecorrelation_heatmap.png",sep=""), width = 3, height = 7, dpi = 600)


####Trait Correlation Plots

traitmodules3 <- traitmodules2 %>%
  filter(as.numeric(MMpvalue) <= 0.05)

i <- 1

module = as.character(traitmodules3$module[i])
module_label=traitmodules3$position_label[i]
print(i)
print(paste(module))
#module = "red"
correlation <- round(as.numeric(traitmodules3$cor[i]),3)
pvalue <- round(as.numeric(traitmodules3$MMpvalue[i]),6)
column = match(module, modNames);
moduleGenes = moduleColors==module; 
sizeGrWindow(7, 7);
par(mfrow = c(1,1));

xvalues <- tryCatch(abs(geneModuleMembership[moduleGenes, column]),
                error = function(e) { skip_to_next <<- TRUE}) 
yvalues <- abs(geneTraitSignificance[moduleGenes, 1])
ngenes <- length(xvalues)

ggplot_df <- as.data.frame(cbind(xvalues,yvalues))

p <- ggplot(ggplot_df,aes(xvalues,yvalues,color=module)) +
  geom_point(size=5) +
  scale_color_identity() +
  xlab(paste("Module Membership in", module_label)) +
                   ylab("Gene significance for trait") +
  ggtitle(paste(module_label,"(n = ",ngenes,", cor = ",correlation,", p = ",pvalue,")",sep="")) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        plot.title = element_text(size = rel(1.2), hjust = 0.5, face="bold",margin=margin(0,0,0,0)),
        axis.title = element_text(size = rel(1.4), face="bold"),
        axis.text.y = element_text(size = rel(1.4), face="bold"),
        axis.text.x = element_text(size = rel(1.4), face="bold"),
              #panel.grid = element_line(color = "lightgray",size = 0.75),
        legend.position="right",
        legend.title=element_blank(),
        legend.text=element_blank(), 
        plot.margin = unit(c(0,0,0,0), "cm"))

ggsave(plot = print(p),paste(outputdir,"/TUCR_Database/",trait_id,"/10_6_",trait_id,"_",module_label,".png",sep=""),height=5,width=5)

i <- 2

module = as.character(traitmodules3$module[i])
module_label=traitmodules3$position_label[i]
print(i)
print(paste(module))
#module = "red"
correlation <- round(as.numeric(traitmodules3$cor[i]),3)
pvalue <- round(as.numeric(traitmodules3$MMpvalue[i]),6)
column = match(module, modNames);
moduleGenes = moduleColors==module; 
sizeGrWindow(7, 7);
par(mfrow = c(1,1));

xvalues <- tryCatch(abs(geneModuleMembership[moduleGenes, column]),
                error = function(e) { skip_to_next <<- TRUE}) 
yvalues <- abs(geneTraitSignificance[moduleGenes, 1])
ngenes <- length(xvalues)

ggplot_df <- as.data.frame(cbind(xvalues,yvalues))

p <- ggplot(ggplot_df,aes(xvalues,yvalues,color=module)) +
  geom_point(size=5) +
  scale_color_identity() +
  xlab(paste("Module Membership in", module_label)) +
                   ylab("Gene significance for trait") +
  ggtitle(paste(module_label,"(n = ",ngenes,", cor = ",correlation,", p = ",pvalue,")",sep="")) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        plot.title = element_text(size = rel(1.2), hjust = 0.5, face="bold",margin=margin(0,0,0,0)),
        axis.title = element_text(size = rel(1.4), face="bold"),
        axis.text.y = element_text(size = rel(1.4), face="bold"),
        axis.text.x = element_text(size = rel(1.4), face="bold"),
              #panel.grid = element_line(color = "lightgray",size = 0.75),
        legend.position="right",
        legend.title=element_blank(),
        legend.text=element_blank(), 
        plot.margin = unit(c(0,0,0,0), "cm"))

ggsave(plot = print(p),paste(outputdir,"/TUCR_Database/",trait_id,"/10_5_",trait_id,"_",module_label,".png",sep=""),height=5,width=5)


i <- 3

module = as.character(traitmodules3$module[i])
module_label=traitmodules3$position_label[i]
print(i)
print(paste(module))
#module = "red"
correlation <- round(as.numeric(traitmodules3$cor[i]),3)
pvalue <- round(as.numeric(traitmodules3$MMpvalue[i]),6)
column = match(module, modNames);
moduleGenes = moduleColors==module; 
sizeGrWindow(7, 7);
par(mfrow = c(1,1));

xvalues <- tryCatch(abs(geneModuleMembership[moduleGenes, column]),
                error = function(e) { skip_to_next <<- TRUE}) 
yvalues <- abs(geneTraitSignificance[moduleGenes, 1])
ngenes <- length(xvalues)

ggplot_df <- as.data.frame(cbind(xvalues,yvalues))

p <- ggplot(ggplot_df,aes(xvalues,yvalues,color=module)) +
  geom_point(size=5) +
  scale_color_identity() +
  xlab(paste("Module Membership in", module_label)) +
                   ylab("Gene significance for trait") +
  ggtitle(paste(module_label,"(n = ",ngenes,", cor = ",correlation,", p = ",pvalue,")",sep="")) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        plot.title = element_text(size = rel(1.2), hjust = 0.5, face="bold",margin=margin(0,0,0,0)),
        axis.title = element_text(size = rel(1.4), face="bold"),
        axis.text.y = element_text(size = rel(1.4), face="bold"),
        axis.text.x = element_text(size = rel(1.4), face="bold"),
              #panel.grid = element_line(color = "lightgray",size = 0.75),
        legend.position="right",
        legend.title=element_blank(),
        legend.text=element_blank(), 
        plot.margin = unit(c(0,0,0,0), "cm"))

ggsave(plot = print(p),paste(outputdir,"/TUCR_Database/",trait_id,"/10_4_",trait_id,"_",module_label,".png",sep=""),height=5,width=5)


i <- length(traitmodules3$module)

module = as.character(traitmodules3$module[i])
module_label=traitmodules3$position_label[i]
print(i)
print(paste(module))
#module = "red"
correlation <- round(as.numeric(traitmodules3$cor[i]),3)
pvalue <- round(as.numeric(traitmodules3$MMpvalue[i]),6)
column = match(module, modNames);
moduleGenes = moduleColors==module; 
sizeGrWindow(7, 7);
par(mfrow = c(1,1));

xvalues <- tryCatch(abs(geneModuleMembership[moduleGenes, column]),
                error = function(e) { skip_to_next <<- TRUE}) 
yvalues <- abs(geneTraitSignificance[moduleGenes, 1])
ngenes <- length(xvalues)

ggplot_df <- as.data.frame(cbind(xvalues,yvalues))

p <- ggplot(ggplot_df,aes(xvalues,yvalues,color=module)) +
  geom_point(size=5) +
  scale_color_identity() +
  xlab(paste("Module Membership in", module_label)) +
                   ylab("Gene significance for trait") +
  ggtitle(paste(module_label,"(n = ",ngenes,", cor = ",correlation,", p = ",pvalue,")",sep="")) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        plot.title = element_text(size = rel(1.2), hjust = 0.5, face="bold",margin=margin(0,0,0,0)),
        axis.title = element_text(size = rel(1.4), face="bold"),
        axis.text.y = element_text(size = rel(1.4), face="bold"),
        axis.text.x = element_text(size = rel(1.4), face="bold"),
              #panel.grid = element_line(color = "lightgray",size = 0.75),
        legend.position="right",
        legend.title=element_blank(),
        legend.text=element_blank(), 
        plot.margin = unit(c(0,0,0,0), "cm"))

ggsave(plot = print(p),paste(outputdir,"/TUCR_Database/",trait_id,"/10_1_",trait_id,"_",module_label,".png",sep=""),height=5,width=5)


i <- length(traitmodules3$module)-1

module = as.character(traitmodules3$module[i])
module_label=traitmodules3$position_label[i]
print(i)
print(paste(module))
#module = "red"
correlation <- round(as.numeric(traitmodules3$cor[i]),3)
pvalue <- round(as.numeric(traitmodules3$MMpvalue[i]),6)
column = match(module, modNames);
moduleGenes = moduleColors==module; 
sizeGrWindow(7, 7);
par(mfrow = c(1,1));

xvalues <- tryCatch(abs(geneModuleMembership[moduleGenes, column]),
                error = function(e) { skip_to_next <<- TRUE}) 
yvalues <- abs(geneTraitSignificance[moduleGenes, 1])
ngenes <- length(xvalues)

ggplot_df <- as.data.frame(cbind(xvalues,yvalues))

p <- ggplot(ggplot_df,aes(xvalues,yvalues,color=module)) +
  geom_point(size=5) +
  scale_color_identity() +
  xlab(paste("Module Membership in", module_label)) +
                   ylab("Gene significance for trait") +
  ggtitle(paste(module_label,"(n = ",ngenes,", cor = ",correlation,", p = ",pvalue,")",sep="")) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        plot.title = element_text(size = rel(1.2), hjust = 0.5, face="bold",margin=margin(0,0,0,0)),
        axis.title = element_text(size = rel(1.4), face="bold"),
        axis.text.y = element_text(size = rel(1.4), face="bold"),
        axis.text.x = element_text(size = rel(1.4), face="bold"),
              #panel.grid = element_line(color = "lightgray",size = 0.75),
        legend.position="right",
        legend.title=element_blank(),
        legend.text=element_blank(), 
        plot.margin = unit(c(0,0,0,0), "cm"))

ggsave(plot = print(p),paste(outputdir,"/TUCR_Database/",trait_id,"/10_2_",trait_id,"_",module_label,".png",sep=""),height=5,width=5)


i <- length(traitmodules3$module)-2

module = as.character(traitmodules3$module[i])
module_label=traitmodules3$position_label[i]
print(i)
print(paste(module))
#module = "red"
correlation <- round(as.numeric(traitmodules3$cor[i]),3)
pvalue <- round(as.numeric(traitmodules3$MMpvalue[i]),6)
column = match(module, modNames);
moduleGenes = moduleColors==module; 
sizeGrWindow(7, 7);
par(mfrow = c(1,1));

xvalues <- tryCatch(abs(geneModuleMembership[moduleGenes, column]),
                error = function(e) { skip_to_next <<- TRUE}) 
yvalues <- abs(geneTraitSignificance[moduleGenes, 1])
ngenes <- length(xvalues)

ggplot_df <- as.data.frame(cbind(xvalues,yvalues))

p <- ggplot(ggplot_df,aes(xvalues,yvalues,color=module)) +
  geom_point(size=5) +
  scale_color_identity() +
  xlab(paste("Module Membership in", module_label)) +
                   ylab("Gene significance for trait") +
  ggtitle(paste(module_label,"(n = ",ngenes,", cor = ",correlation,", p = ",pvalue,")",sep="")) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(), 
        axis.line = element_line(colour = "black"),
        plot.title = element_text(size = rel(1.2), hjust = 0.5, face="bold",margin=margin(0,0,0,0)),
        axis.title = element_text(size = rel(1.4), face="bold"),
        axis.text.y = element_text(size = rel(1.4), face="bold"),
        axis.text.x = element_text(size = rel(1.4), face="bold"),
              #panel.grid = element_line(color = "lightgray",size = 0.75),
        legend.position="right",
        legend.title=element_blank(),
        legend.text=element_blank(), 
        plot.margin = unit(c(0,0,0,0), "cm"))

ggsave(plot = print(p),paste(outputdir,"/TUCR_Database/",trait_id,"/10_3_",trait_id,"_",module_label,".png",sep=""),height=5,width=5)

}
```

```{r}
sessionInfo()
```



Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

